---
title: "AP_UKAlc_Exploratory_Plots"
author: "Anna Patterson"
date: "2024-01-12"
output: html_document
---



#raincloud plots on raw variables on interest from am_data
```{r}
#Alc amt - interesting
ggplot(am_data, aes(1, Alc_Amt_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())   
#Feel Drunk - potentially interesting 
ggplot(am_data, aes(1, Alc_Drunk_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())  
#Alc urge - not interesting
ggplot(am_data, aes(1, Urg_Alc_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Nic urge - not interesting
ggplot(am_data, aes(1, Urg_Nic_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Mar urge - not interesting
ggplot(am_data, aes(1, Urg_Mar_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Coc urge - not interesting 
ggplot(am_data, aes(1, Urg_Coc_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Oth urge - not interesting 
ggplot(am_data, aes(1, Urg_Oth_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Alc Crave - interesting 
ggplot(am_data, aes(1, Crav_Alc_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Mar Crave - interesting 
ggplot(am_data, aes(1, Crav_Mar_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Coc Crave - not interesting 
ggplot(am_data, aes(1, Crav_Coc_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Benz Crave - not interesting 
ggplot(am_data, aes(1, Crav_Benz_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Hall Crave - not interesting 
ggplot(am_data, aes(1, Crav_Hall_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Opiate Crav - not interesting 
ggplot(am_data, aes(1, Crav_Opiate_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
```


#Day of the week analysis 
```{r}
#weekend defined as Saturday/Sunday (so indicates amount Fri/Sat bc amts are for the night before)
am_data_weekend <- am_data %>%
  filter(wday(daterated) %in% c(1, 7))
am_data_weekday <- am_data %>%
  filter(wday(daterated) %in% c(2, 3, 4, 5, 6))
#Alc Amt
ggplot(am_data_weekend, aes(1, Alc_Amt_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
ggplot(am_data_weekend, aes(1, Alc_Amt_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
Alc_Amt_am_model_weekend <- lmer(Alc_Amt_am~ (1 | ID),
                                 data = am_data_weekend)
summary(Alc_Amt_am_model_weekend)
icc(Alc_Amt_am_model_weekend) 
ggplot(am_data_weekday, aes(1, Alc_Amt_am)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
ggplot(am_data_weekday, aes(1, Alc_Amt_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
Alc_Amt_am_model_weekday <- lmer(Alc_Amt_am~ (1 | ID),
                                 data = am_data_weekday)
summary(Alc_Amt_am_model_weekday)
icc(Alc_Amt_am_model_weekday) 
##alc amt stats by day of week 
#Saturday (actually indicates Friday)
am_data_Sat <- am_data %>%
  filter(wday(daterated) %in% c(7))
summary(am_data_Sat$Alc_Amt_am, na.rm =T)
#Sunday (actually indicates Saturday)
am_data_Sun <- am_data %>%
  filter(wday(daterated) %in% c(1))
summary(am_data_Sun$Alc_Amt_am, na.rm =T)
#Monday (actually indicates Sunday)
am_data_Mon <- am_data %>%
  filter(wday(daterated) %in% c(2))
summary(am_data_Mon$Alc_Amt_am, na.rm =T)
#Tuesday (actually indicates Monday)
am_data_Tues <- am_data %>%
  filter(wday(daterated) %in% c(3))
summary(am_data_Tues$Alc_Amt_am, na.rm =T)
#Wednesday (actually indicates Tuesday)
am_data_Wed <- am_data %>%
  filter(wday(daterated) %in% c(4))
summary(am_data_Wed$Alc_Amt_am, na.rm =T)
#Thursday (actually indicates Wednesday)
am_data_Thurs <- am_data %>%
  filter(wday(daterated) %in% c(5))
summary(am_data_Thurs$Alc_Amt_am, na.rm =T)
#Friday (actually indicates Thursday)
am_data_Fri <- am_data %>%
  filter(wday(daterated) %in% c(6))
summary(am_data_Fri$Alc_Amt_am, na.rm =T) 
###Plots by Day of Week 
ggplot(am_data, aes(x = factor(DayOfWeek), y = Alc_Amt_am)) +
  geom_point(position = position_jitter(width = 0.1), size = 1) +
  labs(x = "Day of the Week", y = "Number of Drinks") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
ggplot(am_data, aes(x = factor(DayOfWeek), y = Alc_Amt_am.d)) +
  geom_boxplot() +
  labs(x = "Day of the Week", y = "Number of Drinks") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))

```
#Binge drinks per day (subtract one day for each bc surveys are filled out next day)
```{r}
#number of people who binge drank on Saturdays = 53
am_data_Sun %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
#number of people who binge drank on Sundays = 15
am_data_Mon %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
#number of people who binge drank on Mondays = 21
am_data_Tues %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
#number of people who binge drank on Tuesdays = 15
am_data_Wed %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
#number of people who binge drank on Wednesdays = 16
am_data_Thurs %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
#number of people who binge drank on Thursdays = 24
am_data_Fri %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
#number of people who binge drank on Fridays = 38
am_data_Sat %>% group_by(ID) %>% 
  filter(Alc_Amt_am >= 4) 
```

#raincloud plots on person-centered variables on interest from am_data
```{r}
#Alc amt - interesting
ggplot(am_data, aes(1, Alc_Amt_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())
#Feel Drunk - interesting 
ggplot(am_data, aes(1, Alc_Drunk_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank())   
#Alc urge - interesting
ggplot(am_data, aes(1, Urg_Alc_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Nic urge - potentially interesting
ggplot(am_data, aes(1, Urg_Nic_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Mar urge - interesting
ggplot(am_data, aes(1, Urg_Mar_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Coc urge - not interesting 
ggplot(am_data, aes(1, Urg_Coc_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Oth urge - not interesting 
ggplot(am_data, aes(1, Urg_Oth_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Alc Crave - interesting 
#Would be interesting to compare difference between crav_alc and urg_alc? 
ggplot(am_data, aes(1, Crav_Alc_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Mar Crave - interesting 
ggplot(am_data, aes(1, Crav_Mar_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Coc Crave - not interesting 
ggplot(am_data, aes(1, Crav_Coc_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Benz Crave - not interesting 
ggplot(am_data, aes(1, Crav_Benz_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Hall Crave - not interesting 
ggplot(am_data, aes(1, Crav_Hall_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Opiate Crav - not interesting 
ggplot(am_data, aes(1, Crav_Opiate_am.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
```


## IF OUTCOME IS LINEAR, function is "lmer" not "glmer"
# rest of syntax is the same, including * for interaction and placement of random effect terms
model6 <- lmer(DMQsocial_today~legalage+age.z+covidrestrictions+
                                   currentdx_SUDalc+currentdx_SUDnonalc+frisatsun+
                                   LH_perimenstrual_count+LH_midluteal_count+LH_midfol_LH
                                 +(1+LH_midluteal_count+
                                     LH_midfol_LH+
                                     LH_perimenstrual_count | id), 
                                 control=lmerControl(optimizer="optimx",
                                                     optCtrl=list(method='nlminb')),
                                 data = etoh_data_motives)
#Create ICC for each variable that showed high variability on rainclouds from am_data 
```{r}
#calculate interclass correlations within person for each possible outcome (0 means all w/in person variance, 1 is between person variance) 
#Alc Urg ICC 0.266 
Urg_Alc_am_model <- lmer(Urg_Alc_am~ (1 | ID),
                                 data = am_data)
summary(Urg_Alc_am_model)
icc(Urg_Alc_am_model) 
#Alc Drunk ICC 0.742
Alc_Drunk_am_model <- lmer(Alc_Drunk_am~ (1 | ID),
                                 data = am_data)
summary(Alc_Drunk_am_model)
icc(Alc_Drunk_am_model) 
#Alc Crav ICC 0.617 
Crav_Alc_am_model <- lmer(Crav_Alc_am~ (1 | ID),
                                 data = am_data)
summary(Crav_Alc_am_model)
icc(Crav_Alc_am_model) 
#Alc Amt ICC 0.274
Alc_Amt_am_model <- lmer(Alc_Amt_am~ (1 | ID),
                                 data = am_data)
summary(Alc_Amt_am_model)
icc(Alc_Amt_am_model) 
#Mar crav ICC 0.741
Crav_Mar_am_model <- lmer(Crav_Mar_am~ (1 | ID),
                                 data = am_data)
summary(Crav_Mar_am_model)
icc(Crav_Mar_am_model) 

#Mar urg ICC 0.763
Urg_Mar_am_model <- lmer(Urg_Mar_am~ (1 | ID),
                                 data = am_data)
summary(Urg_Mar_am_model) 
icc(Urg_Mar_am_model) 
```


#PM Data by Day of Week 
```{r}
#Saturday (actually indicates Friday)
pm_data_Sat <- pm_data %>%
  filter(wday(daterated) %in% c(7))
summary(pm_data_Sat$Urg_Alc_pm, na.rm =T) #alc urge mean = 2.4 on Fridays 
summary(pm_data_Sat$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = 0.34 on Fridays 
summary(pm_data_Sat$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.2 on Fridays 
#Sunday (actually indicates Saturday)
pm_data_Sun <- pm_data %>%
  filter(wday(daterated) %in% c(1))
summary(pm_data_Sun$Urg_Alc_pm, na.rm =T) #alc urge mean = 1.85 on Saturdays 
summary(pm_data_Sun$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = -0.067 on Saturdays
summary(pm_data_Sun$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.1 on Saturdays
#Monday (actually indicates Sunday)
pm_data_Mon <- pm_data %>%
  filter(wday(daterated) %in% c(2))
summary(pm_data_Mon$Urg_Alc_pm, na.rm =T) #alc urge mean = 1.75 on Sundays
summary(pm_data_Mon$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = -0.21 on Sundays
summary(pm_data_Mon$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.2 on Sundays 
#Tuesday (actually indicates Monday)
pm_data_Tues <- pm_data %>%
  filter(wday(daterated) %in% c(3))
summary(pm_data_Tues$Urg_Alc_pm, na.rm =T) #alc urge mean = 1.99 on Mondays
summary(pm_data_Tues$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = -0.24 on Mondays
summary(pm_data_Tues$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.1 on Mondays
#Wednesday (actually indicates Tuesday)
pm_data_Wed <- pm_data %>%
  filter(wday(daterated) %in% c(4))
summary(pm_data_Wed$Urg_Alc_pm, na.rm =T) #alc urge mean = 1.93 on Tuesdays 
summary(pm_data_Wed$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = -0.15 on Mondays
summary(pm_data_Wed$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.1 on Tuesdays 
#Thursday (actually indicates Wednesday)
pm_data_Thurs <- pm_data %>%
  filter(wday(daterated) %in% c(5))
summary(pm_data_Thurs$Urg_Alc_pm, na.rm =T) #alc urge mean = 2.5 on Wednesdays 
summary(pm_data_Thurs$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = 0.24 on Mondays
summary(pm_data_Thurs$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.1 on Tuesdays 
#Friday (actually indicates Thursday)
pm_data_Fri <- pm_data %>%
  filter(wday(daterated) %in% c(6))
summary(pm_data_Fri$Urg_Alc_pm, na.rm =T) #alc urge mean = 2.25 on Thursdays
summary(pm_data_Fri$Urg_Alc_pm.d, na.rm =T) #person-centered alc urge mean = 0.035 on Thursdays 
summary(pm_data_Fri$Diff_Inhib_pm, na.rm =T) #diff inhib mean = 1.2 on Thursdays  
###Plots by Day of Week 
ggplot(pm_data, aes(x = factor(DayOfWeek), y = Urg_Alc_pm)) +
  geom_point(position = position_jitter(width = 0.1), size = 1) +
  labs(x = "Day of the Week", y = "Urge to Drink") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
ggplot(pm_data, aes(x = factor(DayOfWeek), y = Urg_Alc_pm.d)) +
  geom_boxplot() +
  labs(x = "Day of the Week", y = "Urge to Drink") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
ggplot(pm_data, aes(x = factor(DayOfWeek), y = Diff_Inhib_pm.d)) +
  geom_boxplot() +
  labs(x = "Day of the Week", y = "Difficulty with Inhibition") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
ggplot(pm_data, aes(x = factor(DayOfWeek), y = Diff_Stop_pm.d)) +
  geom_boxplot() +
  labs(x = "Day of the Week", y = "Difficulty with Stopping") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
ggplot(pm_data, aes(x = factor(DayOfWeek), y = Res_Urge_pm.d)) +
  geom_boxplot() +
  labs(x = "Day of the Week", y = "Difficulty with Resisting Fun Urge") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
ggplot(pm_data, aes(x = factor(DayOfWeek), y = Diff_ResRew_pm.d)) +
  geom_boxplot() +
  labs(x = "Day of the Week", y = "Difficulty with Immediate Reward") +
  scale_x_discrete(labels = c("Sun", "Mon", "Tue", "Wed", "Thu", "Fri", "Sat"))
```


ICCs for pm_data
```{r}
#Alc urge ICC 0.442 
Urg_Alc_pm_model <- lmer(Urg_Alc_pm~ (1 | ID),
                                 data = pm_data)
summary(Urg_Alc_pm_model)
icc(Urg_Alc_pm_model) 
#Nic urge ICC 0.770 
Urg_Nic_pm_model <- lmer(Urg_Nic_pm~ (1 | ID),
                                 data = pm_data)
summary(Urg_Nic_pm_model)
icc(Urg_Nic_pm_model) 
#Mar urge ICC 0.657
Urg_Mar_pm_model <- lmer(Urg_Mar_pm~ (1 | ID),
                                 data = pm_data)
summary(Urg_Mar_pm_model)
icc(Urg_Mar_pm_model) 
#Coc urge ICC 0.979 
Urg_Coc_pm_model <- lmer(Urg_Coc_pm~ (1 | ID),
                                 data = pm_data)
summary(Urg_Coc_pm_model)
icc(Urg_Coc_pm_model) 
#Diff inhib ICC 0.183 
Diff_Inhib_pm_model <- lmer(Diff_Inhib_pm~ (1 | ID),
                                 data = pm_data)
summary(Diff_Inhib_pm_model)
icc(Diff_Inhib_pm_model) 
#Diff change ICC 0.300
Diff_Change_pm_model <- lmer(Diff_Change_pm~ (1 | ID),
                                 data = pm_data)
summary(Diff_Change_pm_model)
icc(Diff_Change_pm_model) 
#Diff stop ICC 0.135
Diff_Stop_pm_model <- lmer(Diff_Stop_pm~ (1 | ID),
                                 data = pm_data)
summary(Diff_Stop_pm_model)
icc(Diff_Stop_pm_model) 
#Immed payoff ICC 0.271
Immed_Payoff_pm_model <- lmer(Immed_Payoff_pm~ (1 | ID),
                                 data = pm_data)
summary(Immed_Payoff_pm_model)
icc(Immed_Payoff_pm_model) 
#Res urge ICC 0.425
Res_Urge_pm_model <- lmer(Res_Urge_pm~ (1 | ID),
                                 data = pm_data)
summary(Res_Urge_pm_model)
icc(Res_Urge_pm_model) 
#Diff LongRew ICC 0.294 
Diff_LongRew_pm_model <- lmer(Diff_LongRew_pm~ (1 | ID),
                                 data = pm_data)
summary(Diff_LongRew_pm_model)
icc(Diff_LongRew_pm_model) 
#Diff ResRew ICC 0.278
Diff_ResRew_pm_model <- lmer(Diff_ResRew_pm~ (1 | ID),
                                 data = pm_data)
summary(Diff_ResRew_pm_model)
icc(Diff_ResRew_pm_model) 
#Depression ICC 0.221
Dep_pm_model <- lmer(Dep_pm~ (1 | ID),
                                 data = pm_data)
summary(Dep_pm_model)
icc(Dep_pm_model) 
#Hopeless ICC 0.174
Hopeless_pm_model <- lmer(Hopeless_pm~ (1 | ID),
                                 data = pm_data)
summary(Hopeless_pm_model)
icc(Hopeless_pm_model) 
#Worthless icc 0.280 
Worthless_pm_model <- lmer(Worthless_pm~ (1 | ID),
                                 data = pm_data)
summary(Worthless_pm_model)
icc(Worthless_pm_model) 
#Anxious icc 0.511 
Anxious_pm_model <- lmer(Anxious_pm~ (1 | ID),
                                 data = pm_data)
summary(Anxious_pm_model)
icc(Anxious_pm_model) 
#Moodswing icc 0.154
MoodSwing_pm_model <- lmer(MoodSwing_pm~ (1 | ID),
                                 data = pm_data)
summary(MoodSwing_pm_model)
icc(MoodSwing_pm_model) 
#RejSens icc 0.230 
RejSens_pm_model <- lmer(RejSens_pm~ (1 | ID),
                                 data = pm_data)
summary(RejSens_pm_model)
icc(RejSens_pm_model) 
#Angry icc 0.230 
Angry_pm_model <- lmer(Angry_pm~ (1 | ID),
                                 data = pm_data)
summary(Angry_pm_model)
icc(Angry_pm_model) 
#Conflicts icc 0.120
Conflicts_pm_model <- lmer(Conflicts_pm~ (1 | ID),
                                 data = pm_data)
summary(Conflicts_pm_model)
icc(Conflicts_pm_model) 
#Loss interest 0.259 
Loss_Interest_pm_model <- lmer(Loss_Interest_pm~ (1 | ID),
                                 data = pm_data)
summary(Loss_Interest_pm_model)
icc(Loss_Interest_pm_model) 
#Diff Conc icc 0.237 
Diff_Conc_pm_model <- lmer(Diff_Conc_pm~ (1 | ID),
                                 data = pm_data)
summary(Diff_Conc_pm_model)
icc(Diff_Conc_pm_model) 
#Tired icc 0.370
Tired_pm_model <- lmer(Tired_pm~ (1 | ID),
                                 data = pm_data)
summary(Tired_pm_model)
icc(Tired_pm_model)
#overeat icc 0.205 
OverEat_pm_model <- lmer(OverEat_pm~ (1 | ID),
                                 data = pm_data)
summary(OverEat_pm_model)
icc(OverEat_pm_model)
#spec food craving 0.147 
Sp_Food_Crav_pm_model <- lmer(Sp_Food_Crav_pm~ (1 | ID),
                                 data = pm_data)
summary(Sp_Food_Crav_pm_model)
icc(Sp_Food_Crav_pm_model)
#high sleep icc 0.195 
High_Sleep_pm_model <- lmer(High_Sleep_pm~ (1 | ID),
                                 data = pm_data)
summary(High_Sleep_pm_model)
icc(High_Sleep_pm_model)
#Overwhelm icc 0.211
Overwhelm_pm_model <- lmer(Overwhelm_pm~ (1 | ID),
                                 data = pm_data)
summary(Overwhelm_pm_model)
icc(Overwhelm_pm_model)
#Loss control icc 0.259 
Loss_Control_pm_model <- lmer(Loss_Control_pm~ (1 | ID),
                                 data = pm_data)
summary(Loss_Control_pm_model)
icc(Loss_Control_pm_model)
#Breast tend icc 0.161 
Breast_Tend_pm_model <- lmer(Breast_Tend_pm~ (1 | ID),
                                 data = pm_data)
summary(Breast_Tend_pm_model)
icc(Breast_Tend_pm_model)
#Breast swell icc 0.253 
Breast_Swell_pm_model <- lmer(Breast_Swell_pm~ (1 | ID),
                                 data = pm_data)
summary(Breast_Swell_pm_model)
icc(Breast_Swell_pm_model)
#Headache icc 0.274
Headache_pm_model <- lmer(Headache_pm~ (1 | ID),
                                 data = pm_data)
summary(Headache_pm_model)
icc(Headache_pm_model)
#JM Pain icc 0.222
JM_Pain_pm_model <- lmer(JM_Pain_pm~ (1 | ID),
                                 data = pm_data)
summary(JM_Pain_pm_model)
icc(JM_Pain_pm_model)
#Loss Prod icc 0.236 
Loss_Prod_pm_model <- lmer(Loss_Prod_pm~ (1 | ID),
                                 data = pm_data)
summary(Loss_Prod_pm_model)
icc(Loss_Prod_pm_model)
#Int relat icc 0.111
Int_Relat_pm_model <- lmer(Int_Relat_pm~ (1 | ID),
                                 data = pm_data)
summary(Int_Relat_pm_model)
icc(Int_Relat_pm_model)
```

#Raincloud plots on raw pm_data
```{r}
#Urg alc - interesting 
ggplot(pm_data, aes(1, Urg_Alc_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Urg nic - not interesting 
ggplot(pm_data, aes(1, Urg_Nic_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Urg mar - interesting 
ggplot(pm_data, aes(1, Urg_Mar_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Urg coc - not interesting 
ggplot(pm_data, aes(1, Urg_Coc_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff inhib - not interesting 
ggplot(pm_data, aes(1, Diff_Inhib_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff stop - not interesting 
ggplot(pm_data, aes(1, Diff_Stop_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff change - not interesting 
ggplot(pm_data, aes(1, Diff_Change_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Immed Payoff - kinda interesting 
ggplot(pm_data, aes(1, Immed_Payoff_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Res urge - kinda interesting 
ggplot(pm_data, aes(1, Res_Urge_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff longrew - not interesting 
ggplot(pm_data, aes(1, Diff_LongRew_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff resrew - not interesting 
ggplot(pm_data, aes(1, Diff_ResRew_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Dep - not interesting 
ggplot(pm_data, aes(1, Dep_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Hopeless - not interesting 
ggplot(pm_data, aes(1, Hopeless_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Worthless - not interesting 
ggplot(pm_data, aes(1, Worthless_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#MoodSwing - not interesting 
ggplot(pm_data, aes(1, MoodSwing_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#RejSens - not interesting 
ggplot(pm_data, aes(1, RejSens_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Angry - not interesting 
ggplot(pm_data, aes(1, Angry_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#LossInt - not interesting 
ggplot(pm_data, aes(1, Loss_Interest_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#DiffConc - not interesting 
ggplot(pm_data, aes(1, Diff_Conc_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Tired  - interesting ! 
ggplot(pm_data, aes(1, Tired_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Overeat  - not interesting 
ggplot(pm_data, aes(1, OverEat_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Spec Food Crav
ggplot(pm_data, aes(1, Sp_Food_Crav_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Angry - interesting 
ggplot(pm_data, aes(1, Angry_pm)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
```

#Raincloud plots for person-centered deviations 
```{r}
#Urg alc - interesting 
ggplot(pm_data, aes(1, Urg_Alc_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#OverEat - interesting 
ggplot(pm_data, aes(1, OverEat_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff Inhib - not interesting 
ggplot(pm_data, aes(1, Diff_Inhib_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff Change - not interesting 
ggplot(pm_data, aes(1, Diff_Change_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff Stop - not interesting 
ggplot(pm_data, aes(1, Diff_Stop_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Immed Payoff - interesting 
ggplot(pm_data, aes(1, Immed_Payoff_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Res Urge - not super interesting 
ggplot(pm_data, aes(1, Res_Urge_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff LongRew - not interesting 
ggplot(pm_data, aes(1, Diff_LongRew_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Depression - interesting 
ggplot(pm_data, aes(1, Dep_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Hopeless - not interesting 
ggplot(pm_data, aes(1, Hopeless_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Worthless - not interesting 
ggplot(pm_data, aes(1, Worthless_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#MoodSwing - interesting 
ggplot(pm_data, aes(1, MoodSwing_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#RejSens - not interesting 
ggplot(pm_data, aes(1, RejSens_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Angry - interesting 
ggplot(pm_data, aes(1, Angry_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Loss intereset - not interesting 
ggplot(pm_data, aes(1, Loss_Interest_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff conc
ggplot(pm_data, aes(1, Diff_Conc_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Diff conc - interesting 
ggplot(pm_data, aes(1, Tired_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Over-eating - interesting 
ggplot(pm_data, aes(1, OverEat_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Spec food craving - interesting 
ggplot(pm_data, aes(1, Sp_Food_Crav_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Overwhelm - not interesting 
ggplot(pm_data, aes(1, Overwhelm_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Loss control - not interesting 
ggplot(pm_data, aes(1, Loss_Control_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Breast tend - not interesting 
ggplot(pm_data, aes(1, Breast_Tend_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Breast swell - not interesting 
ggplot(pm_data, aes(1, Breast_Swell_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Headache - not interesting 
ggplot(pm_data, aes(1, Headache_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#JM Pain - not interesting 
ggplot(pm_data, aes(1, JM_Pain_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Loss prod - not interesting 
ggplot(pm_data, aes(1, Loss_Prod_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Interpersonal Relat- not interesting 
ggplot(pm_data, aes(1, Int_Relat_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
#Urg alc - interesting 
ggplot(pm_data, aes(1, Urg_Mar_pm.d)) +
  geom_rain() +
  theme_classic() +
  theme(axis.title.x = element_blank(), 
        axis.text.x = element_blank(), axis.ticks.x = element_blank()) 
```

