---
title: "UKAlc_JB_plots"
author: "Jordan Barone"
date: "`r Sys.Date()`"
output: html_document
---

#Setup:
-data
-libraries
-wd
```{r}
library(haven) #for reading files
library(ggplot2) #for plotting
library(tidyverse) #for data management and manipulation
library(zoo) #for rolling averages
library(performance) #icc
library(nlme) #for mlm
library(lme4) #for mlm
library(GLMMadaptive) #for testing if study duration is a predictor of outcomes, via "adaptive quadrature"
library(lubridate) #for working with dates
library(broom.mixed) #95% confint
library(readr)
library(tidyr)

knitr::opts_knit$set(root.dir = "~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/") 

```

## import the clean dataset
```{r}
df <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/UKAlc.LH.Data.csv")

hormones <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_HORM/02_data_prep_workspace/Salivary_Hormones_StudyDays.csv")

cycleday.am.merge <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/Cycle_Day_LH_menses_am_labvisit.csv")

```
##JB: data wrangling to plot firstdayofperiod
```{r}
cycleday.am.merge %>% filter(ID == 101) %>%
  select(ID, daterated, Period.Start.Date) %>% print(n=65)


#first problem is that "Period.Start.Date" is just a text entry in one random row, not in the long format of dataset
cycleday.am.merge$Period.Start.Date <- as.Date(cycleday.am.merge$Period.Start.Date, format = "%m/%d/%y")

cycleday.am.merge <- cycleday.am.merge %>%
  group_by(ID) %>%
  #this step fills in the rows starting from the Period.Start.Date until the end of the daterated
  complete(daterated = seq(min(coalesce(Period.Start.Date, min(daterated, na.rm = TRUE))),
                           max(daterated, na.rm = TRUE),
                           by = "1 day")) %>%
  #this step fills Period.Start.Date by ID, since one person's period start date is a trait-level variable
  fill(Period.Start.Date, .direction = "updown") %>%
  #switch to rowwise instead of grouped df for next step
  rowwise() %>%
  #now edit firstdayofperiod 0-1 variable to say that if we get to a row where the daterated matches the reported Period.Start.Date, make firstdayofperiod==1, otherwise keep it as it was
  mutate(firstdayofperiod= ifelse(daterated==Period.Start.Date, 1, firstdayofperiod)) %>%
  #get rid of all the rows of daterated that don't fit between first Period.Start.Date and end of study
  filter(!is.na(daterated))



```

###AP: should we just delete lines 68-100? 
## plot daily hormones, lab visit data against period start date and ov date for verification     
```{r}
saliva_cycleday_merge_am <- merge(hormones, cycleday.am.merge, by = c("ID", "day_in_study"), all = T)
selected_columns <- saliva_cycleday_merge_am[, c("ID", "ovpos", "E2", "P4", "LH", "firstdayofperiod", "day_in_study", "daterated")]

#Create new dataframe with daily hormones and menses/ov data 
hormone_comparison <- data.frame(selected_columns)
hormone_comparison$E2 <- hormone_comparison$E2
hormone_comparison$H_LH <- hormone_comparison$LH
hormone_comparison$H_P4 <- hormone_comparison$P4

#Create plot per ID 
horm_compare_long <- pivot_longer(hormone_comparison, cols = starts_with("H_"), names_to = "variable", values_to = "value")

#make variables numeric 
horm_compare_long$day_in_study <- as.numeric(horm_compare_long$day_in_study)
horm_compare_long$value <- as.numeric(horm_compare_long$value)
horm_compare_long$E2 <- as.numeric(horm_compare_long$E2)
horm_compare_long$daterated <- ymd(horm_compare_long$daterated)
# Plot using ggplot2
horm_compare_long %>% 
  filter(ID==101) %>% 
ggplot() +
  geom_line(aes(x = daterated, y = value, color = variable, group = variable)) +
  geom_line(aes(x = daterated, y = E2*100, color = "E2")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="estradiol")) +
  labs(x = "date", y = "hormone level") +
  theme_minimal() + 
  ggtitle("101") +
  geom_vline(aes(xintercept=ifelse(ovpos==1, daterated, NA)), linetype = "dashed") 

    
```

## another way to try to plot daily hormones, lab visit data against period start date and ov date for verification     
```{r}
saliva_cycleday_merge_am <- merge(hormones, cycleday.am.merge, by = c("ID", "day_in_study"), all = T)

saliva_cycleday_merge_am$H_LH <- saliva_cycleday_merge_am$LH
saliva_cycleday_merge_am$H_P4 <- saliva_cycleday_merge_am$P4

#Create plot per ID 
saliva_cycleday_merge_am <- pivot_longer(saliva_cycleday_merge_am, cols = starts_with("H_"), names_to = "variable", values_to = "value")

#make variables numeric 
saliva_cycleday_merge_am$day_in_study <- as.numeric(saliva_cycleday_merge_am$day_in_study)
saliva_cycleday_merge_am$value <- as.numeric(saliva_cycleday_merge_am$value)
saliva_cycleday_merge_am$E2 <- as.numeric(saliva_cycleday_merge_am$E2)
saliva_cycleday_merge_am$daterated <- ymd(saliva_cycleday_merge_am$daterated)
# Plot using ggplot2
saliva_cycleday_merge_am %>% 
  filter(ID==101) %>% 
ggplot() +
  geom_line(aes(x = daterated, y = value, color = variable, group = variable)) +
  geom_line(aes(x = daterated, y = E2*100, color = "E2")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="estradiol")) +
  labs(x = "date", y = "hormone level") +
  theme_minimal() + 
  ggtitle("101",
          subtitle = "dotted line = menses onset, dashed line = posLH test") +
  geom_vline(aes(xintercept=ifelse(ovpos==1, daterated, NA)), linetype = "dashed") +
  geom_vline(aes(xintercept=ifelse(firstdayofperiod==1, daterated, NA)), linetype = "dotted")
    
```

#make list and perform graphing function on all IDs 
```{r}
#make list of IDs for which to graph hormone data 
#omitted IDs 104, 110, 111, 116, 120, 142, 144, 153, 158 for insufficient data 

ids <- c(101, 102, 103, 105, 106, 107, 108, 109, 112, 113, 114, 115, 117, 118, 119, 121, 122, 123, 124, 125, 126, 128, 129, 130, 131, 133, 134, 135, 136, 138, 139, 140, 141, 143, 145, 146, 147, 148, 149, 150, 152, 154, 155, 156, 157, 159, 160, 161, 162, 163, 164, 165, 166, 167, 168, 169, 170, 171, 172, 173, 174, 175, 176, 177, 178, 179, 180, 181, 182, 183, 184, 185)

for (i in ids) {
  
  #make empty list to store the plots
  plots <- list()
  
  #store and save one plot at a time
  plot <- saliva_cycleday_merge_am %>%  
  filter(ID==i) %>%
  ggplot() +
  geom_line(aes(x = daterated, y = value, color = variable, group = variable)) +
  geom_line(aes(x = daterated, y = E2*100, color = "E2")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="estradiol")) +
  labs(x = "date", y = "hormone level") +
  theme_minimal() + 
  ggtitle(i,
          subtitle = "dotted line = menses onset, dashed line = posLH test") +
  geom_vline(aes(xintercept=ifelse(ovpos==1, daterated, NA)), linetype = "dashed") +
  geom_vline(aes(xintercept=ifelse(firstdayofperiod==1, daterated, NA)), linetype = "dotted") 
  
  #save the plot we just made into the list
  plots[[i]] <- plot
  #print to console
  print(plot)
  
  UKAlc_menses_ov_horm_plots <- paste0("UKAlc_daily_cleaning_plots/UKAlc_menses_ov_horm_plots", i, ".png") 
  ggsave(UKAlc_menses_ov_horm_plots, plot, width = 8, height = 6, dpi = 300) }
#how to save above to box? I just copy/pasted from my local repository into ~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_HORM
```


## JB: create hybridcycleday (one variable combining data surrounding LH and surrounding menses)
```{r}
#create hybrid version of cycle day:
df <- df %>%
  mutate(hybridcycleday = case_when((daycountLH >= -7 & daycountLH <= 15) ~ 
                                      paste(as.character(daycountLH), "L", sep = ""),
                                    (cycleday >= -9 & cycleday <= 10) ~ paste(as.character(cycleday), "M",  sep = ""),
                                    TRUE ~ NA_character_))

am_data_hybridcycleday <- df %>%
  filter(!is.na(hybridcycleday))

hybridcycleday_order <- c("-7L",
                       "-6L",
                       "-5L",
                       "-4L",
                       "-3L",
                       "-2L",
                       "-1L",
                       "0L",
                       "1L",
                       "2L",
                       "3L",
                       "4L",
                       "5L",
                       "6L",
                       "7L",
                       "8L",
                       "9L",
                       "10L",
                       "11L",
                       "12L",
                       "13L",
                       "14L",
                       "15L",
                       "-9M",
                       "-8M",
                       "-7M",
                       "-6M",
                       "-5M",
                       "-4M",
                       "-3M",
                       "-2M",
                       "-1M",
                       "1M",
                       "2M",
                       "3M",
                       "4M",
                       "5M",
                       "6M",
                       "7M",
                       "8M",
                       "9M",
                       "10M")

##hybridcycledayorder if we remove the early M days
hybridcycleday_order_new <- c("-7L",
                       "-6L",
                       "-5L",
                       "-4L",
                       "-3L",
                       "-2L",
                       "-1L",
                       "0L",
                       "1L",
                       "2L",
                       "3L",
                       "4L",
                       "5L",
                       "6L",
                       "7L",
                       "8L",
                       "9L",
                       "10L",
                       "11L",
                       "12L",
                       "13L",
                       "14L",
                       "15L",
                       "2M",
                       "3M",
                       "4M",
                       "5M",
                       "6M",
                       "7M",
                       "8M",
                       "9M",
                       "10M")


#we never have data that does not get overridden by LH count up until menses+2:
am_data_hybridcycleday <- am_data_hybridcycleday %>%
  filter(!hybridcycleday %in% c("-9M",
                       "-8M",
                       "-7M",
                       "-6M",
                       "-5M",
                       "-4M",
                       "-3M",
                       "-2M",
                       "-1M",
                       "1M"))


#craete overall probability of drinking
am_data_hybridcycleday <- am_data_hybridcycleday %>%
  group_by(ID) %>%
  mutate(drinkingprob.m = sum(drink_today_am, na.rm = TRUE)/n())

#create am_data_daycountLH 
am_data_daycountLH <- (cycleday.am.merge) %>% filter(!is.na(daycountLH))



#view everyones overall probability of drinking (on a day that received a cycle variable)
#am_data_cycleday %>% group_by(ID) %>% slice(1) %>% select(ID, drinkingprob.m) ###Anna: I commented this out here bc it doesn't appear to be relevant to my dataset right now 11/29/23. The setup of cycle day variables was named am_data_hybridcycleday 

am_data_hybridcycleday %>% group_by(ID) %>% slice(1) %>% select(ID, drinkingprob.m)

#person-mean-center
data_cycleday_plot <- am_data_hybridcycleday %>%
  group_by(ID, hybridcycleday) %>%
  summarize(drinkingprob.m=mean(drinkingprob.m),
            drinkingprob.day.m = mean(drink_today_am, na.rm = TRUE),
            drinkingdayprob.d = drinkingprob.day.m - drinkingprob.m) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order_new))


```



```{r}


data_cycleday_plot %>% group_by(hybridcycleday) %>%
  summarize(personcentered.dev = mean(drinkingdayprob.d, na.rm=T),
            se=sd(drinkingdayprob.d, na.rm=T)/sqrt(n())) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order_new)) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  ggplot(aes(x=factor(hybridcycleday, levels = hybridcycleday_order_new), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  #geom_vline(xintercept = "1M", col="blue", size=0.25)+
  #geom_vline(xintercept = "0L", col="blue", size=0.25)+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  xlab("Cycle Day (based on LH-surge and menses self-report)")+
  ylab("Person-Centered Prob. of Drinking")

##Anna on 11/29/23: This plot does not hang around zero as expected - likely due to NAs rather than zeros? The NAs are brought about when we extrapolate cycle dates on days surveys were not completed. 
```

## JB: repeat prior block but on daycountLH to see if we get better coverage of the luteal phase
```{r}

#person-mean-center: daycountLH
data_daycountLH_plot <- am_data_hybridcycleday %>% 
  filter(!is.na(daycountLH)) %>%
  group_by(ID, daycountLH) %>% 
  summarize(drinkingprob.m=mean(drinkingprob.m),
            drinkingprob.day.m = mean(drink_today_am, na.rm = TRUE),
            drinkingdayprob.d = drinkingprob.day.m - drinkingprob.m) 

#person-mean-center:menses
data_mensescountplot <- am_data_cycleday %>% group_by(ID, cycleday) %>% 
  filter(!is.na(cycleday)) %>%
  summarize(drinkingprob.m=mean(drinkingprob.m),
            drinkingprob.day.m = mean(drink_today_am, na.rm = TRUE),
            drinkingdayprob.d = drinkingprob.day.m - drinkingprob.m) 


#daycountLH only
data_daycountLH_plot %>% group_by(daycountLH) %>%
  summarize(personcentered.dev = mean(drinkingdayprob.d, na.rm=T),
            se=sd(drinkingdayprob.d, na.rm=T)/sqrt(n())) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  ggplot(aes(x=as.factor(daycountLH), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  xlab("Cycle Day (based on LH-surge only)")+
  ylab("Person-Centered Prob. of Drinking")

#menses count only
data_mensescountplot %>% group_by(cycleday) %>%
  summarize(personcentered.dev = mean(drinkingdayprob.d, na.rm=T),
            se=sd(drinkingdayprob.d, na.rm=T)/sqrt(n())) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  ggplot(aes(x=as.factor(cycleday), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  xlab("Cycle Day (based on menses onset only)")+
  ylab("Person-Centered Prob. of Drinking")

```

## troubleshoot the centering issue
```{r}

am_data_cycleday %>% filter(ID=="101") %>% nrow()

am_data_cycleday %>% filter(ID=="101") %>% 
  filter(drink_today_am==1) %>%
    nrow()

am_data_cycleday %>% filter(ID=="101") %>%
  

9/50

am_data_cycleday %>% filter(ID=="101") %>% filter(hybridcycleday=="-7L") %>% select(daycountLH, drink_today_am, drinkingprob.m)

am_data_cycleday %>% filter(hybridcycleday=="-7L") %>% select(daycountLH, drink_today_am, drinkingprob.m)


test <- am_data_cycleday %>% 
  filter(!is.na(hybridcycleday)) %>%
  group_by(ID, hybridcycleday) %>%
  summarize(drinkingprob.m=mean(drinkingprob.m),
            drinkingprob.day.m = mean(drink_today_am, na.rm = TRUE),
            drinkingdayprob.d = drinkingprob.day.m - drinkingprob.m) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order_new))


test %>% group_by(hybridcycleday) %>%
  summarize(personcentered.dev = mean(drinkingdayprob.d, na.rm=T),
            se=sd(drinkingdayprob.d, na.rm=T)/sqrt(n())) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order_new))


###figure out what the issues are with the dataset
cycleday.am.merge %>% filter(!is.na(Second.Period.Start.Date)) %>%
  filter(Second.Period.Start.Date!= "N/A") # no second period for anyone before 148

##pts with 2 period start dates
twoperiods <- cycleday.am.merge %>% 
  mutate(ID = as.numeric(ID)) %>%
  filter(ID >= 148) 

twoperiods %>% select(ID, daterated, Alc_Amt_am, firstdayofperiod, cycleday)


cycleday.am.merge %>%
  filter(ID >= 148) %>%
  filter(!is.na(StressDay_am)) %>%
  select(ID, daterated, Period.Start.Date, Second.Period.Start.Date, firstdayofperiod,cycleday, StressDay_am)

```

## can we person-center and plot one other var? maybe numdrinks?
```{r}

#person-mean-center Urg_Alc on each specific day: NOTE, this only needs to be done if there are multiple of the same days per person
data_daycountLH_urg_plot <- am_data_cycleday %>% 
  filter(!is.na(daycountLH)) %>%
  group_by(ID, daycountLH) %>% 
  summarize(Urg_Alc_am.m=Urg_Alc_am.m,
            Urg_Alc_am.day.d = Urg_Alc_am - Urg_Alc_am.m)

##CAN START HERE WITH JUST ONE CYCLE PER PERSON
#Urge to Drink Alcohol 
am_data_hybridcycleday %>%
  group_by(daycountLH) %>%
  summarize(personcentered.dev=mean(Urg_Alc_am.d, na.rm=T),
            se = sd(Urg_Alc_am.d, na.rm=T)/sqrt(n())) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  filter(!is.na(daycountLH)) %>%
  ggplot(aes(x=factor(daycountLH), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  geom_vline(xintercept = "0", col="blue", size=0.25)+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  xlab("Cycle Day (based on LH-surge only)")+
  ylab("Person-Centered Urg to Drink")

#Alcohol Amount
am_data_hybridcycleday %>%
  group_by(daycountLH) %>%
  summarize(personcentered.dev=mean(Alc_Amt_am.d, na.rm=T),
            se = sd(Alc_Amt_am.d, na.rm=T)/sqrt(n())) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  filter(!is.na(daycountLH)) %>%
  ggplot(aes(x=factor(daycountLH), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  geom_vline(xintercept = "0", col="blue", size=0.25)+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  xlab("Cycle Day (based on LH-surge only)")+
  ylab("Person-Centered Amount Alcohol Consumed")
#Alcohol Craving
am_data_hybridcycleday %>%
  group_by(daycountLH) %>%
  summarize(personcentered.dev=mean(Crav_Alc_am.d, na.rm=T),
            se = sd(Crav_Alc_am.d, na.rm=T)/sqrt(n())) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  filter(!is.na(daycountLH)) %>%
  ggplot(aes(x=factor(daycountLH), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  geom_vline(xintercept = "0", col="blue", size=0.25)+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  xlab("Cycle Day (based on LH-surge only)")+
  ylab("Person-Centered Alcohol Craving")

```
## cleaning hormone data
```{r}

#rename vars
hormones <- hormones %>%
  rename(
         samplenum = `day_in_study`,
         Estradiol = `E2`,
         Progesterone = `P4`)

#removed the -1, -2, etc from ID num
hormones <- hormones %>%
  mutate(ID = str_extract(ID, "\\d{3}"))

#pivot to LONG format so that progesterone and LH are contained within one new variable called "Hormone" and the values are stored in "pg_ml
#keep estrogen separate because we will add it on a new axis
hormones <- hormones %>% 
  pivot_longer(cols = c(Progesterone:LH), names_to = "Hormone", values_to = "pg_ml")

```

## plot hormones 
```{r}

hormones %>% 
  filter(ID==145) %>% ##change out the ID number to see each person's hormones
  ggplot(aes(x=samplenum, y=pg_ml, group=Hormone, color=Hormone))+
  geom_line()+
  geom_line(aes(y = Estradiol*100, color = "Estradiol")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="Estradiol")) +
  ggtitle("161")+
  ylab("Progesterone or LH")+
  xlab("sample number")

```
## code to save an individual plot of hormones for everyone!
```{r}

##TO DO: make a list of IDS called "ids"
#ids <- c(145, 146) (just an example)

for (i in ids) {
  
  #make empty list to store the plots
  plots <- list()
  
  #store and save one plot at a time
  plot <- adhd_ky_bio %>%  #change with your dataset
  filter(ID==i) %>%
  ggplot(aes(x=TubeNumber, y=pg_ml, group=Hormone, color=Hormone))+
  geom_line()+
  geom_line(aes(y = Estradiol*100, color = "Estradiol")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="estradiol")) +
    ggtitle(i)
  
  #save the plot we just made into the list
  plots[[i]] <- plot
  #print to console
  print(plot)
  
  file_name <- paste0("2023-05-25 Hormone Graphs_04.11.23 dataset/hormones_plot_", i, ".png") #update name with where you want this to save
  ggsave(file_name, plot, width = 8, height = 6, dpi = 300)
}
```

## Anna trying loop code above, didn't want to erase what Jordan made above 
```{r}

##TO DO: make a list of IDS called "ids"
#ids <- c(145, 146) (just an example)

ids <- c("145", "149", "150", "154", "157", "148", "149", "152", "155", "156", "161", "146", "159", "164", "163", "164", "165", "166", "167", "168", "169", "173", "159", "160", "162", "170", "171", "172", "147", "125")
for (i in ids) {
  
  #make empty list to store the plots
  plots <- list()
  
  #store and save one plot at a time
  plot <- hormones %>%  #change with your dataset
  filter(ID==i) %>%
  ggplot(aes(x=samplenum, y=pg_ml, group=Hormone, color=Hormone))+
  geom_line()+
  geom_line(aes(y = Estradiol*100, color = "Estradiol")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="estradiol")) +
    ggtitle(i)
  
  #save the plot we just made into the list
  plots[[i]] <- plot
  #print to console
  print(plot)
  
  file_name <- paste0("2023-11-29 Hormone Graphs_11.29.23 dataset/hormones_plot_", i, ".png") #update name with where you want this to save
  ggsave(file_name, plot, width = 8, height = 6, dpi = 300)
}
```



==== ALL EXAMPLE CODE BELOW =====
## spaghetti plots by cycle phase (one line per person, person-centered)
```{r}
RR_data_for_plot1a %>% 
  group_by(id, LH_cyclephasenames) %>%
  summarize(person.m.drinkingprob.d = mean(drinkingprobphase.d, na.rm=T),
            se=sd(drinkingprobphase.d, na.rm=T)/sqrt(n())) %>%
  ggplot(aes(x=LH_cyclephasenames, y=person.m.drinkingprob.d, group=id))+
  geom_line()+
  scale_x_discrete(labels=c("midfol" = "Midfollicular", 
                            "midlut" = "Midluteal",
                            "perimen" = "Perimenstrual",
                            "periov" = "Periovulatory"))+
  scale_y_continuous(limits = c(-0.05, 0.10))+
  geom_errorbar(aes(ymin=person.m.drinkingprob.d-se, 
                    ymax=person.m.drinkingprob.d+se), 
                size=0.5, width=0.5, position=position_dodge())+
  geom_hline(yintercept=0.0, color="red", linetype="dashed")+
  theme_bw()+
  xlab("Cycle Phase")+
  ylab("Person-Centered Prob. of Drinking")
```


## outcome by cycle phase (one line, person-centered)
```{r}
RR_data_for_plot1a %>% 
  group_by(LH_cyclephasenames) %>%
  summarize(grand.m.drinkingprob.d = mean(drinkingprobphase.d, na.rm=T),
            se=sd(drinkingprobphase.d, na.rm=T)/sqrt(n())) %>%
  ggplot(aes(x=LH_cyclephasenames, y=grand.m.drinkingprob.d))+
  geom_line(group=1)+
  scale_x_discrete(labels=c("midfol" = "Midfollicular", 
                            "midlut" = "Midluteal",
                            "perimen" = "Perimenstrual",
                            "periov" = "Periovulatory"))+
  scale_y_continuous(limits = c(-0.05, 0.10))+
  geom_errorbar(aes(ymin=grand.m.drinkingprob.d-se, 
                    ymax=grand.m.drinkingprob.d+se), 
                size=0.5, width=0.5, position=position_dodge())+
  geom_hline(yintercept=0.0, color="red", linetype="dashed")+
  theme_bw()+
  xlab("Cycle Phase")+
  ylab("Person-Centered Prob. of Drinking")
```

## outcome by day of week (one line, person-centered)
```{r}
RR_data_for_plot1b <- etoh_data %>% group_by(id, dayofweek) %>% 
  filter(!is.na(dayofweek)) %>%
  summarize(drinkingprob.m=mean(drinkingprob.m),
            drinkingprobdayofweek.m = mean(drinkingday_today, na.rm = TRUE),
            drinkingprobdayofweek.d = drinkingprobdayofweek.m - drinkingprob.m)

#plot1b
RR_PLOT1bpersoncentered_by_dayofweek_line <- RR_data_for_plot1b %>% group_by(dayofweek) %>%
  summarize(grand.m.drinkingprobdayofweek.d = mean(drinkingprobdayofweek.d, na.rm=T),
            se=sd(drinkingprobdayofweek.d, na.rm=T)/sqrt(n())) %>%
  ggplot(aes(x=as.factor(dayofweek), y=grand.m.drinkingprobdayofweek.d))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  geom_errorbar(aes(ymin=grand.m.drinkingprobdayofweek.d-se, 
                    ymax=grand.m.drinkingprobdayofweek.d+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  scale_x_discrete(breaks=c(1,2,3,4,5,6,7),
                   labels=c("Sun", "Mon", "Tues", 
                            "Wed", "Thurs", "Fri", "Sat"))+
  xlab("Day of Week")+
  ylab("Person-Centered Prob. of Drinking")
```

## outcome by cycle day (one line, person-centered)
```{r}

#create hybrid version of cycle day:
etoh_data_cycleday <- etoh_data_cycleday %>%
  mutate(hybridcycleday = case_when((daycountLH >= -7 & daycountLH <= 5) ~ 
                                      paste(as.character(daycountLH), "L", sep = ""),
                                    (cycleday >= -9 & cycleday <= 7) ~ 
                                      paste(as.character(cycleday), "M",  sep = ""),
                                    TRUE ~ NA_character_))

etoh_data_cycleday <- etoh_data_cycleday %>%
  filter(!is.na(hybridcycleday))

hybridcycleday_order <- c("-7L",
                       "-6L",
                       "-5L",
                       "-4L",
                       "-3L",
                       "-2L",
                       "-1L",
                       "0L",
                       "1L",
                       "2L",
                       "3L",
                       "4L",
                       "5L",
                       "-9M",
                       "-8M",
                       "-7M",
                       "-6M",
                       "-5M",
                       "-4M",
                       "-3M",
                       "-2M",
                       "-1M",
                       "1M",
                       "2M",
                       "3M",
                       "4M",
                       "5M",
                       "6M",
                       "7M")

#person-mean-center
RR_data_for_plot1c <- etoh_data_cycleday %>% group_by(id, hybridcycleday) %>% 
  filter(!is.na(hybridcycleday)) %>%
  summarize(drinkingprob.m=mean(drinkingprob.m),
            drinkingprob.day.m = mean(drinkingday_today, na.rm = TRUE),
            drinkingdayprob.d = drinkingprob.day.m - drinkingprob.m) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order))

RR_PLOT1cpersoncentered_by_day_roll <- 
  RR_data_for_plot1c %>% group_by(hybridcycleday) %>%
  summarize(personcentered.dev = mean(drinkingdayprob.d, na.rm=T),
            se=sd(drinkingdayprob.d, na.rm=T)/sqrt(n())) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order)) %>%
  mutate(roll= rollapply(personcentered.dev, 3, 
                         mean, align = "center", fill=NA)) %>%
  ggplot(aes(x=factor(hybridcycleday, levels = hybridcycleday_order), y=roll))+
  geom_line(group=1)+
  geom_hline(yintercept = 0, linetype="dashed", col="red")+
  #geom_vline(xintercept = "1M", col="blue", size=0.25)+
  #geom_vline(xintercept = "0L", col="blue", size=0.25)+
  geom_errorbar(aes(ymin=roll-se, ymax=roll+se), 
                size=0.5, width=0.5, position=position_dodge())+
  theme_bw()+
  scale_y_continuous(expand = c(0,0.001))+
  xlab("Cycle Day (based on LH-surge and menses self-report)")+
  ylab("Person-Centered Prob. of Drinking")+
  annotate("rect", ymin = -0.065, ymax = -0.055, xmin = "-7L", xmax = "-3L", alpha = .2)+
  annotate("text", x="-7L", y=-0.06, label="midfollicular", 
           size=3, hjust=-0.25, fontface="italic")+
  annotate("rect", ymin = -0.065, ymax = -0.055, xmin = "-2L", xmax = "1L", alpha = .2)+
  annotate("text", x="-2L", y=-0.06, label="periovulatory", 
           size=3, hjust=0, fontface="italic")+
  annotate("rect", ymin = -0.065, ymax = -0.055, xmin = "-9M", xmax = "-5M", alpha = .2)+
  annotate("text", x="-9M", y=-0.06, label="midluteal", 
           size=3, hjust=-0.5, fontface="italic")+
  annotate("rect", ymin = -0.065, ymax = -0.055, xmin = "-3M", xmax = "2M", alpha = .2)+
  annotate("text", x="-3M", y=-0.06, label="perimenstrual", 
           size=3, hjust=-0.15, fontface="italic")+
  annotate("text", x="0L", y=-0.07, label="*", size=8, color="blue")+
  annotate("text", x="1M", y=-0.07, label="*", size=8, color="blue")

```

## outcome by cycle day, separated by weekend and weekday (one line, person centered
)
```{r}
#plot 1d = weekendvsweekday
RR_PLOT1dpersoncentered_by_day_roll <- etoh_data_cycleday %>% 
  group_by(id, hybridcycleday) %>% #each person gets a deviation for that cycleday (x)
  filter(!is.na(hybridcycleday)) %>% #ignore any NAs
  summarize(drinkingprob.m=drinkingprob.m, #that person's overall mean (already calculated, just pulling down)
            drinkingprobday.m = mean(drinkingday_today, na.rm = TRUE), #that person's overall mean
            drinkingprobday.d = drinkingprobday.m - drinkingprob.m, #that person's deviation on cycle day X
            #that persons mean for drinking on that cycle day on weekdays
            drinkingprobday.wd.m = mean(drinkingday_today[frisatsun==0],na.rm=T), 
            #that persons mean for drinking on that cycle day on weekends
            drinkingprobday.we.m = mean(drinkingday_today[frisatsun==1],na.rm = T), 
            #person centered deviation on cycle day X on weekdays
            drinkingprobday.wd.d = drinkingprobday.wd.m - drinkingprob.m,
            #person centered deviation on cycle day X on weekends
            drinkingprobday.we.d = drinkingprobday.we.m - drinkingprob.m) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order)) %>%
  ungroup() %>%
  group_by(hybridcycleday) %>%
  summarize(#grand.m.drinkingprob.m=mean(drinkingprob.m, na.rm=T), 
            #grand.drinkingprob.we=mean(drinkingprob.we.m, na.rm=T),
            #grand.drinkingprob.wd = mean(drinkingprob.wd.m, na.rm=T),
            #mean of all the person-centered deviations, on cycle day X on weekdays
            grand.m.drinkingprobday.wd.d = mean(drinkingprobday.wd.d, na.rm=T),
            #mean of all the person-centered deviations, on cycle day X on weekends
            grand.m.drinkingprobday.we.d = mean(drinkingprobday.we.d, na.rm=T),
            se.wd = sd(drinkingprobday.wd.d, na.rm=T)/sqrt(n()),
            se.we = sd(drinkingprobday.we.d, na.rm=T)/sqrt(n())) %>%
  arrange(factor(hybridcycleday, levels = hybridcycleday_order)) %>%
  #make the rolling average based on the mean of the deviations, for w.e. and w.d. separately
  mutate(roll.wd = rollapply(grand.m.drinkingprobday.wd.d, 3, 
                         mean, align = "center", fill=NA),
         roll.we = rollapply(grand.m.drinkingprobday.we.d, 3, 
                         mean, align = "center", fill=NA)) %>%
  ggplot()+
  geom_line(aes(x=factor(hybridcycleday, levels = hybridcycleday_order), y=roll.wd), group=1, color="red")+
  geom_ribbon(aes(x=factor(hybridcycleday, levels = hybridcycleday_order),
                    ymin=roll.wd-se.wd,
                    ymax=roll.wd+se.wd),
              fill="red", alpha=0.5, group=1)+
  geom_line(aes(x=factor(hybridcycleday, levels = hybridcycleday_order), y=roll.we), group=1, color="blue")+
  geom_ribbon(aes(x=factor(hybridcycleday, levels = hybridcycleday_order),
                    ymin=roll.we-se.we,
                    ymax=roll.we+se.we),
              fill="blue", alpha=0.5, group=1)+
  theme_bw()+
  theme(axis.title.x = element_blank())+
  ggtitle("Person-centered Probability to Drink by Cycle Day",
          subtitle = "Centered on Overall Mean")+
  ylab("Deviation from Participant Mean")+
  annotate("text",  x="-6M", y = 0.13, label = "Fri-Sun", color="blue")+
  annotate("text",  x="-6M", y = -0.13, label = "Mon-Thurs", color="red")+
  geom_hline(yintercept = 0.0, color="black", linetype="dashed")+
  annotate("rect", ymin = 0.01, ymax = 0.02, xmin = "-7L", xmax = "-3L", alpha = .2)+
  annotate("text", x="-7L", y=0.015, label="midfollicular", 
           size=3, hjust=-0.25, fontface="italic")+
  annotate("rect", ymin = 0.01, ymax = 0.02, xmin = "-2L", xmax = "1L", alpha = .2)+
  annotate("text", x="-2L", y=0.015, label="periovulatory", 
           size=3, hjust=0, fontface="italic")+
  annotate("rect", ymin = 0.01, ymax = 0.02, xmin = "-9M", xmax = "-5M", alpha = .2)+
  annotate("text", x="-9M", y=0.015, label="midluteal", 
           size=3, hjust=-0.5, fontface="italic")+
  annotate("rect", ymin = 0.01, ymax = 0.02, xmin = "-3M", xmax = "2M", alpha = .2)+
  annotate("text", x="-3M", y=0.015, label="perimenstrual", 
           size=3, hjust=-0.15, fontface="italic")
```

## plot hormone levels by person (one plot per id)
```{r}

adhd_ky_bio %>% 
  filter(ID==260) %>%                              
  ggplot(aes(x=TubeNumber, y=pg_ml, group=Hormone, color=Hormone))+
  geom_line()+
  geom_line(aes(y = Estradiol*100, color = "Estradiol")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="estradiol")) +
  ggtitle("260")

rollingavgs <- adhd_ky_bio %>% 
  group_by(Hormone, ID) %>%
  mutate(Estradiol.roll = rollapply(Estradiol, 3, mean,na.rm = TRUE, fill = NA),
         Hormone.roll = rollapply(pg_ml, 3, mean,na.rm = TRUE, fill = NA))

figfortheorypaper <- rollingavgs %>%
  filter(ID==260) %>%                              
  ggplot(aes(x=TubeNumber, y=Hormone.roll, group=Hormone, color=Hormone, linetype = Hormone))+
  geom_line()+
  ylab("Progesterone, LH (pg/ml)")+
  xlab("Day")+
  scale_x_continuous(breaks = c(0,5,10,15,20,25,30))+
  geom_line(aes(y = Estradiol.roll*100, color = "Estradiol", linetype = "Estradiol")) +
    scale_y_continuous(sec.axis = sec_axis(~./100, name="Estradiol (pg/ml)")) +
  ggtitle("Daily hormone levels from a representative ovulating participant")+
  theme_bw()+
  theme(legend.position = "bottom")
```

