---
title: "UKAlc_Merging_Descriptives"
author: "Anna Patterson"
date: "2023-09-28"
output: html_document
---

rm(list = ls())
```{r}
#libraries
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(janitor)
knitr::opts_chunk$set(echo = TRUE)

#Anisha's Paths


# am_qual <- read.csv("C:/Users/anish/Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/AM_Qualtrics_csv.csv")
# 
# pm_qual <- read.csv("C:/Users/anish/Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/PM_Qualtrics_csv.csv")
# 
# am_rc <- read.csv("C:/Users/anish/Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/AM_REDCap_csv.csv")
# 
# pm_rc <- read.csv("C:/Users/anish/Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/PM_REDCap_csv.csv")


#Anna's Paths

am_qual <- read.csv("/Users/apatte21/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/AM_Qualtrics_csv.csv")

pm_qual <- read.csv("/Users/apatte21/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/PM_Qualtrics_csv.csv")

am_rc <- read.csv("/Users/apatte21/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/AM_REDCap_csv.csv")

pm_rc <- read.csv("/Users/apatte21/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/PM_REDCap_csv.csv")
```

ID's in am_qual: 101 102 103 104 105 106 107 108 109 110 111 112 113 114 115 116 117 118 119 120 121 122 126

ID's in a_rc: [1] "123"       "124"       "125"       "125b"      "125c"      "125d"      "127"       "127 (new)" "128"      
[10] "129"       "130"       "131"       "132"       "133"       "134"       "134b"      "135"       "136"      
[19] "138"       "139"       "139b"      "140"       "141"       "142"       "142b"      "143"       "144"      
[28] "145"       "146"       "147"       "148"       "149"       "150"       "152"       "153"       "154"      
[37] "155"       "156"       "157"       "158"       "159"       "160"       "161"       "162"       "163"      
[46] "164"       "165"       "166"       "166a"      "166b"      "167"       "168"       "169"       "170"      
[55] "171"       "172"       "173"       "174"       "175"       "176"       "177"       "178"       "179"      
[64] "180"       "181"       "182"       "183"       "184"       "185"   

ID's in pm_qual: 101 102 103 104 105 106 107 108 109 111 112 113 114 115 116 117 118 119 120 121 122 126 

ID's in pm_rc: [1] "123"       "124"       "125"       "125b"      "125c"      "125d"      "127"       "127 (new)" "128"      
[10] "129"       "130"       "131"       "132"       "133"       "134"       "134b"      "135"       "136"      
[19] "138"       "139"       "139b"      "140"       "141"       "142"       "142b"      "143"       "144"      
[28] "145"       "146"       "147"       "148"       "149"       "150"       "152"       "153"       "154"      
[37] "155"       "156"       "157"       "158"       "159"       "160"       "161"       "162"       "163"      
[46] "164"       "165"       "166"       "166a"      "166b"      "167"       "168"       "169"       "170"      
[55] "171"       "172"       "173"       "174"       "175"       "176"       "177"       "178"       "179"      
[64] "180"       "181"       "182"       "183"       "184"       "185"    



#IDs in am qualtrics are numerical, IDs in rc are string form -- letters at end of some IDs indicate different sessions of same participant 
```{r}
am_data <- merge(am_qual, am_rc, by = c("ID", "DateTime"), all = T)

pm_data <- merge(pm_qual, pm_rc, by = c("ID", "DateTime"), all = T)

```
#view overlap between am and pm data 
#See how many unique IDs are in each dataset 
```{r}
intersect(am_data$ID, pm_data$ID)

setdiff(am_data$ID, pm_data$ID)

am_pm_part <- intersect(am_data$ID, pm_data$ID)
length(am_pm_part)

am_data$ID <- gsub("[^0-9.-]", "", am_data$ID)
pm_data$ID <- gsub("[^0-9.-]", "", pm_data$ID)

#seeing how many IDs are in each data set, viewed the output and saw they included NA in the calculation, so subtracted 1 from final calculation 
length(unique(am_data$ID))
length(unique(pm_data$ID))
```

#Before correcting for duplicates, we have n = 83 for am data and n = 82 for pm data 

```{r}
#separate datetime variable 
am_data[c('daterated', 'time')] <- str_split_fixed(am_data$DateTime, ' ', 2)
pm_data[c('daterated', 'time')] <- str_split_fixed(pm_data$DateTime, ' ', 2)
```

```{r}
#Transform daterated into a date variable so R can recognize as date variable
am_data$daterated <- lubridate::mdy(am_data$daterated)
pm_data$daterated <- lubridate::mdy(pm_data$daterated)

#Remove DateTime column from df 
am_data = subset(am_data, select = -c(DateTime))
pm_data = subset(pm_data, select = -c(DateTime))
```

```{r}
replace_empty_with_na <- function(data) {
  data %>% mutate_if(is.character, ~ ifelse(. == "", NA, .))
}

# Replace empty strings with NA in your dataset
# data1 <- replace_empty_with_na(data1)
# data2 <- replace_empty_with_na(data2)

xymerge <- function(dat) {
  # Create a logical vector indicating which column names end in ".x"
  x_cols <- grepl("\\.x$", names(dat))
  
  # Loop over each x column and apply the ifelse function
  for (x_col in names(dat)[x_cols]) {
    # Extract the corresponding y column name
    y_col <- gsub("\\.x$", ".y", x_col)
    
    # Create a new column name by removing the .x suffix
    new_col <- gsub("\\.x$", "", x_col)
    
    # Apply the ifelse function to the x and y columns and assign the result to the new column
    dat[[new_col]] <- ifelse(is.na(dat[[x_col]]), dat[[y_col]], dat[[x_col]])
    
    # Remove the x and y columns from the dataframe
    dat[[x_col]] <- NULL
    dat[[y_col]] <- NULL
  }
  
  # Return the updated data frame
  return(dat)
}

#replace empty with NA so they're coded the same for subsequent functions 
am_data <- replace_empty_with_na(am_data)
pm_data <- replace_empty_with_na(pm_data)
#consolidate xy variable names that existed as a byproduct of merging the two datasets with the same column names
am_data <- xymerge(am_data)
pm_data <- xymerge(pm_data)
```

#relocate daterated to be after ID and remove time column 
```{r}
am_data <- am_data %>% 
  relocate(daterated, .after = ID) 
pm_data <- pm_data %>% 
  relocate(daterated, .after = ID) 

```



```{r}
#Add _am and _pm suffixes to each dataset 
colnames(am_data) <- paste(colnames(am_data), "am", sep="_")

colnames(pm_data) <- paste(colnames(pm_data), "pm", sep="_")
```

```{r}
#rename daterated and ID to drop the _am and _pm suffixes 
colnames(am_data)[colnames(am_data) == "daterated_am"] ="daterated"
colnames(pm_data)[colnames(pm_data) == "daterated_pm"] ="daterated"

colnames(am_data)[colnames(am_data) == "ID_am"] ="ID"
colnames(pm_data)[colnames(pm_data) == "ID_pm"] ="ID"
```


#Remove rows where everything is NA except daterated, time, and ID
```{r}
# am_data <- am_data %>%
#   filter(!is.na(ID) | !is.na(daterated) | !is.na(time_am))
# conflicts_prefer(dplyr::filter) 
# 
# pm_data <- pm_data %>%
#   filter(!is.na(ID) | !is.na(daterated) | !is.na(time_pm))
# conflicts_prefer(dplyr::filter) 

#Anna tried the above code 10/11/23, no change to either df but perhaps no rows fit this criteria 

am_data <- am_data %>% drop_na(daterated, ID)
pm_data <- pm_data %>% drop_na(daterated, ID)

```

#Find Duplicates in Dates per ID 
```{r}

result.am <- am_data %>%
  group_by(ID, daterated) %>%
  summarise(observations = n())

dupdate_am <- subset(result.am, observations != 1)

result.pm <- pm_data %>%
  group_by(ID, daterated) %>%
  summarise(observations = n())

dupdate_pm <- subset(result.pm, observations != 1)

```

#Remove rows so that we no longer have >1 submission per am or pm data per date. Kept earliest timestamp if all submissions are identical, or kept most complete form if some are more completed than others. 
```{r}
#remove duplicates for 106 on 2021-05-09 
am_data %>%
  filter(ID == 106 & daterated == ymd("2021-05-09"))

am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-09" & am_data$time_am == "10:02"), ]
am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-09" & am_data$time_am == "9:59"), ]

#remove duplicates for 106 on 2021-05-18 
am_data %>%
  filter(ID == 106 & daterated == ymd("2021-05-18"))

am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-18" & am_data$time_am == "6:35"), ]

#remove duplicates for 106 on 2021-05-20 
am_data %>%
  filter(ID == 106 & daterated == ymd("2021-05-20"))

am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-20" & am_data$time_am == "4:50"), ]

#remove duplicates for 106 on 2021-05-24 
am_data %>%
  filter(ID == 106 & daterated == ymd("2021-05-24"))

am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-24" & am_data$time_am == "21:59"), ]
am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-24" & am_data$time_am == "22:00"), ]
am_data <- am_data[!(am_data$ID == 106 & am_data$daterated == "2021-05-24" & am_data$time_am == "22:02"), ]

#remove duplicates for 112 on 2021-06-28 
am_data %>%
  filter(ID == 112 & daterated == ymd("2021-06-28"))

am_data <- am_data[!(am_data$ID == 112 & am_data$daterated == "2021-06-28" & am_data$time_am == "4:58"), ]

#remove duplicates for 112 on 2021-07-11
am_data %>%
  filter(ID == 112 & daterated == ymd("2021-07-11"))

am_data <- am_data[!(am_data$ID == 112 & am_data$daterated == "2021-07-11" & am_data$time_am == "18:38"), ] 

#remove duplicates for 113 on 2021-06-23 
am_data %>%
  filter(ID == 113 & daterated == ymd("2021-06-23"))

am_data <- am_data[!(am_data$ID == 113 & am_data$daterated == "2021-06-23" & am_data$time_am == "14:34"), ] 

#remove duplicates for 113 on 2021-07-07 
am_data %>%
  filter(ID == 113 & daterated == ymd("2021-07-07"))

am_data <- am_data[!(am_data$ID == 113 & am_data$daterated == "2021-07-07" & am_data$time_am == "11:57"), ] 

#remove duplicates for 113 on 2021-07-21
am_data %>%
  filter(ID == 113 & daterated == ymd("2021-07-21"))

am_data <- am_data[!(am_data$ID == 113 & am_data$daterated == "2021-07-21" & am_data$time_am == "11:12"), ] 

#remove duplicates for 114 on 2021-06-29
am_data %>%
  filter(ID == 114 & daterated == ymd("2021-06-29"))

am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-06-29" & am_data$time_am == "22:00"), ] 

#remove duplicates for 114 on 2021-07-01 
am_data %>%
  filter(ID == 114 & daterated == ymd("2021-07-01"))

am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-07-01 " & am_data$time_am == "9:33"), ] 

#remove duplicates for 114 on 2021-07-04 
am_data %>%
  filter(ID == 114 & daterated == ymd("2021-07-04"))

am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-07-04" & am_data$time_am == "5:58"), ] 

#remove duplicates for 114 on 2021-07-06
am_data %>%
  filter(ID == 114 & daterated == ymd("2021-07-06"))

am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-07-06" & am_data$time_am == "4:52"), ] 

#remove duplicates for 114 on 2021-07-09 
am_data %>%
  filter(ID == 114 & daterated == ymd("2021-07-09"))

am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-07-09" & am_data$time_am == "21:44"), ] 
am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-07-09" & am_data$time_am == "21:45"), ] 

#remove duplicates for 114 on 2021-07-15
am_data %>%
  filter(ID == 114 & daterated == ymd("2021-07-15"))

am_data <- am_data[!(am_data$ID == 114 & am_data$daterated == "2021-07-15" & am_data$time_am == "7:44"), ] 

#remove duplicates for 115 on 2021-06-24 
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-06-24"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-06-24" & am_data$time_am == "6:52"), ] 

#remove duplicates for 115 on 2021-06-27
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-06-27"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-06-27" & am_data$time_am == "8:27"), ] 

#remove duplicates for 115 on 2021-07-01
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-07-01"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-01" & am_data$time_am == "19:53"), ] 

#remove duplicates for 115 on 2021-07-04
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-07-04"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-04" & am_data$time_am == "3:00"), ] 

#remove duplicates for 115 on 2021-07-09 
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-07-09"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-09" & am_data$time_am == "21:49"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-09" & am_data$time_am == "21:52"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-09" & am_data$time_am == "21:55"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-09" & am_data$time_am == "22:01"), ] 

#remove duplicates for 115 on 2021-07-11
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-07-11"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-11" & am_data$time_am == "8:38"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-11" & am_data$time_am == "8:41"), ] 

#remove duplicates for 115 on 2021-07-20 
am_data %>%
  filter(ID == 115 & daterated == ymd("2021-07-20"))

am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "6:50"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "6:57"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "7:00"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "7:04"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "7:06"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "7:09"), ] 
am_data <- am_data[!(am_data$ID == 115 & am_data$daterated == "2021-07-20" & am_data$time_am == "7:13"), ] 

#remove duplicates for 118 on 2021-08-08
am_data %>%
  filter(ID == 118 & daterated == ymd("2021-08-08"))

am_data <- am_data[!(am_data$ID == 118 & am_data$daterated == "2021-08-08" & am_data$time_am == "12:29"), ] 

#remove duplicates for 119 on 2021-08-27
am_data %>%
  filter(ID == 119 & daterated == ymd("2021-08-27"))

am_data <- am_data[!(am_data$ID == 119 & am_data$daterated == "2021-08-27" & am_data$time_am == "21:42"), ] 

#remove duplicates for 123 on 2021-08-31
am_data %>%
  filter(ID == 123 & daterated == ymd("2021-08-31"))

am_data <- am_data[!(am_data$ID == 123 & am_data$daterated == "2021-08-31" & am_data$time_am == "5:05"), ] 

#remove duplicates for 131 on 2021-10-17 
am_data %>%
  filter(ID == 131 & daterated == ymd("2021-10-17 "))

am_data <- am_data[!(am_data$ID == 131 & am_data$daterated == "2021-10-17" & am_data$time_am == "22:16"), ] 

#remove duplicates for ID 136 on 2021-11-29 
am_data %>%
  filter(ID == 136 & daterated == ymd("2021-11-29"))

am_data <- am_data[!(am_data$ID == 136 & am_data$daterated == "2021-11-29" & am_data$time_am == "12:56"), ] 

#remove duplicates for ID 141 on 2022-02-01
am_data %>%
  filter(ID == 141 & daterated == ymd("2022-02-01"))

am_data <- am_data[!(am_data$ID == 141 & am_data$daterated == "2022-02-01" & am_data$time_am == "7:30"), ] 

#remove duplicates for ID 149 on 2022-06-13
am_data %>%
  filter(ID == 149 & daterated == ymd("2022-06-13"))

am_data <- am_data[!(am_data$ID == 149 & am_data$daterated == "2022-06-13" & am_data$time_am == "13:57"), ] 

#remove duplicates for ID 159 on 2022-07-17
am_data %>%
  filter(ID == 159 & daterated == ymd("2022-07-17"))

am_data <- am_data[!(am_data$ID == 159 & am_data$daterated == "2022-07-17" & am_data$time_am == "9:59"), ] 

#remove duplicates for ID 159 on 2022-08-05
am_data %>%
  filter(ID == 159 & daterated == ymd("2022-08-05"))

am_data <- am_data[!(am_data$ID == 159 & am_data$daterated == "2022-08-05" & am_data$time_am == "9:59"), ] 

#remove duplicates for ID 161 on 2022-08-12
am_data %>%
  filter(ID == 161 & daterated == ymd("2022-08-12"))

am_data <- am_data[!(am_data$ID == 161 & am_data$daterated == "2022-08-12" & am_data$time_am == "6:30"), ] 

#remove duplicates for ID 166 on 2022-09-15
am_data %>%
  filter(ID == 166 & daterated == ymd("2022-09-15"))

am_data <- am_data[!(am_data$ID == 166 & am_data$daterated == "2022-09-15" & am_data$time_am == "10:52"), ] 

#remove duplicates for 171 on 2022-10-21 
am_data %>%
  filter(ID == 171 & daterated == ymd("2022-10-21"))

am_data <- am_data[!(am_data$ID == 171 & am_data$daterated == "2022-10-21" & am_data$time_am == "13:03"), ] 

#remove duplicates for 180 on 2023-03-26
am_data %>%
  filter(ID == 180 & daterated == ymd("2023-03-26"))

am_data <- am_data[!(am_data$ID == 180 & am_data$daterated == "2023-03-26" & am_data$time_am == "2:42"), ] 

#remove duplicates for 181 on 2023-03-22
am_data %>%
  filter(ID == 181 & daterated == ymd("2023-03-22"))

am_data <- am_data[!(am_data$ID == 181 & am_data$daterated == "2023-03-22" & am_data$time_am == "13:46"), ] 
```

#Previous Day Survey Check Before Removing PM Duplicates 

```{r}
#For each duplicate of completed surveys for a person, check if they completed the previous day survey. If they did not, it means they could have meant the earlier time duplicate for the previous day. Rather than excluding these from the study as duplicates, I will re-assign them to the prior day so that we can have the most robust/inclusive dataset possible.

pm_dupes <- pm_data %>% 
  get_dupes(ID, daterated)
pm_data <- pm_data %>%
  left_join(pm_dupes)
pm_data$dupe_count[is.na(pm_data$dupe_count)] <- 0

priordaydupe <- function(x) {
  x$ID <- as.numeric(x$ID)
  x <- x %>% group_by(ID) %>% arrange(daterated)
  y <- x
  count = 0
  n = unique(x$ID)
  for (i in n) {
    iddat <- subset(y, ID == i)
    m = dim(iddat)[1]
    for (j in 1:m) {
      if (!is.na(iddat$dupe_count[j]) && iddat$dupe_count[j] == 2) {
        count = count + 1
        b = (iddat$daterated[j])
        if (!(as.Date(b - 1) %in% iddat$daterated)) {
          print(paste('The survey does not exist for the day before', b, "for the id number", i))
        }
      }
    }
  }
  print(paste('There are', count, 'surveys where the same daterated is recorded, by participant'))
}




priordaydupe(pm_data) 
#This will only work if the date variable is called daterated
```

#Changing Each priordaydup ID daterated to the day prior if one of the dup surveys was before 10:00am (indicates it was meant for day prior)
```{r}
changedatepm <- function(id, time, olddate, newdate){
  pm_data %>%
  mutate(daterated = case_when(
    ID== id & time_pm == time & daterated == mdy(olddate) ~ mdy(newdate),
    TRUE ~ daterated
  ))
  
}
#filter each priordaydupe ID to examine duplicates and changedatepm if applicable 
pm_data%>% filter(ID == 109)%>% select(ID, daterated, time_pm)
#changing 4/20 first dup to 4/19
pm_data <- pm_data %>%
  mutate(daterated = case_when(
    ID== 103 & time_pm == "0:05" & daterated == mdy("4/20/21") ~ mdy("4/19/21"),
    TRUE ~ daterated
  ))

#ID 103 
pm_data <- changedatepm(103, "0:05", "4/20/21","4/19/21")
pm_data <- changedatepm(103, "1:58", "4/24/21","4/23/21")
pm_data <- changedatepm(103, "0:12", "4/26/21","4/25/21")
pm_data <- changedatepm(103, "1:55", "5/09/21","5/08/21")
#ID 105
pm_data <- changedatepm(105, "6:08", "5/09/21","5/08/21")
pm_data <- changedatepm(105, "9:03", "5/07/21","5/06/21")
pm_data <- changedatepm(105, "7:11", "5/13/21","5/12/21")
pm_data <- changedatepm(105, "7:09", "5/18/21","5/17/21")
#ID 106
pm_data <- changedatepm(106, "8:50", "5/12/21","5/11/21")
#ID 107 
pm_data <- changedatepm(107, "4:35", "5/25/21","5/24/21")
pm_data <- changedatepm(107, "5:19", "6/06/21","6/05/21")
#ID 108
pm_data <- changedatepm(108, "0:46", "6/16/21","6/15/21")
pm_data <- changedatepm(108, "9:45", "6/20/21","6/19/21")
#ID 109 
pm_data <- changedatepm(109, "0:08", "6/07/21","6/06/21")
pm_data <- changedatepm(109, "6:17", "6/13/21","6/12/21")
pm_data <- changedatepm(109, "7:44", "6/15/21","6/14/21")
pm_data <- changedatepm(109, "9:48", "6/24/21","6/23/21")
#ID 111
pm_data <- changedatepm(111, "7:11", "6/20/21","6/19/21")
pm_data <- changedatepm(111, "6:34", "6/22/21","6/21/21")
#ID 113 
pm_data <- changedatepm(113, "8:22", "6/18/21","6/17/21")
pm_data <- changedatepm(113, "5:32", "6/20/21","6/19/21")
pm_data <- changedatepm(113, "5:52", "6/23/21","6/22/21")
pm_data <- changedatepm(113, "0:17", "7/06/21","7/05/21")
pm_data <- changedatepm(113, "10:50", "7/11/21","7/10/21")
pm_data <- changedatepm(113, "3:41", "7/14/21","7/13/21")
#ID 114
pm_data <- changedatepm(114, "8:24", "6/20/21","6/19/21")
pm_data <- changedatepm(114, "9:36", "6/25/21","6/24/21")
pm_data <- changedatepm(114, "5:57", "7/04/21","7/03/21")
pm_data <- changedatepm(114, "5:59", "7/04/21","7/03/21")
pm_data <- changedatepm(114, "4:46", "7/06/21","7/05/21")
pm_data <- changedatepm(114, "4:51", "7/06/21","7/05/21")
#ID 112
pm_data%>% filter(ID == 112)%>% select(ID, daterated, time_pm)
pm_data <- changedatepm(112, "7:23", "6/24/21","6/23/21")
pm_data <- changedatepm(112, "4:59", "6/28/21","6/27/21")
pm_data <- changedatepm(112, "0:03", "7/04/21","7/03/21")
#ID 117
pm_data%>% filter(ID == 117)%>% select(ID, daterated, time_pm)
pm_data <- changedatepm(117, "1:12", "7/09/21","7/08/21")
pm_data <- changedatepm(117, "0:38", "7/16/21","7/15/21")
pm_data <- changedatepm(117, "8:36", "7/24/21","7/23/21")
pm_data <- changedatepm(117, "2:11", "7/26/21","7/25/21")
```

[1] "The survey does not exist for the day before 2021-04-20 for the id number 103" #changed

[1] "The survey does not exist for the day before 2021-04-24 for the id number 103" #changed

[1] "The survey does not exist for the day before 2021-04-26 for the id number 103" #changed

[1] "The survey does not exist for the day before 2021-05-09 for the id number 103" #changed

[1] "The survey does not exist for the day before 2021-05-07 for the id number 105" #changed

[1] "The survey does not exist for the day before 2021-05-09 for the id number 105" #changed

[1] "The survey does not exist for the day before 2021-05-13 for the id number 105" #changed

[1] "The survey does not exist for the day before 2021-05-18 for the id number 105" #changed

[1] "The survey does not exist for the day before 2021-05-09 for the id number 106" #unchanged

[1] "The survey does not exist for the day before 2021-05-12 for the id number 106" #changed

[1] "The survey does not exist for the day before 2021-05-14 for the id number 106" #unchanged

[1] "The survey does not exist for the day before 2021-05-20 for the id number 106" #unchanged

[1] "The survey does not exist for the day before 2021-05-25 for the id number 107" #changed

[1] "The survey does not exist for the day before 2021-06-06 for the id number 107" #changed

[1] "The survey does not exist for the day before 2021-06-16 for the id number 108" #changed

[1] "The survey does not exist for the day before 2021-06-20 for the id number 108" #changed

[1] "The survey does not exist for the day before 2021-06-07 for the id number 109" #changed

[1] "The survey does not exist for the day before 2021-06-13 for the id number 109" #changed

[1] "The survey does not exist for the day before 2021-06-15 for the id number 109" #changed

[1] "The survey does not exist for the day before 2021-06-24 for the id number 109" #changed

[1] "The survey does not exist for the day before 2021-06-20 for the id number 111" #changed

[1] "The survey does not exist for the day before 2021-06-22 for the id number 111" #changed

[1] "The survey does not exist for the day before 2021-06-18 for the id number 113" #changed

[1] "The survey does not exist for the day before 2021-06-20 for the id number 113" #changed

[1] "The survey does not exist for the day before 2021-06-23 for the id number 113" #changed

[1] "The survey does not exist for the day before 2021-06-29 for the id number 113" #unchanged

[1] "The survey does not exist for the day before 2021-07-02 for the id number 113" #unchanged

[1] "The survey does not exist for the day before 2021-07-06 for the id number 113" #changed

[1] "The survey does not exist for the day before 2021-07-11 for the id number 113" #changed

[1] "The survey does not exist for the day before 2021-07-14 for the id number 113" #changed

[1] "The survey does not exist for the day before 2021-06-20 for the id number 114" #changed

[1] "The survey does not exist for the day before 2021-06-25 for the id number 114" #changed

[1] "The survey does not exist for the day before 2021-07-04 for the id number 114" #changed

[1] "The survey does not exist for the day before 2021-07-06 for the id number 114" #changed

[1] "The survey does not exist for the day before 2021-07-11 for the id number 114" #unchanged

[1] "The survey does not exist for the day before 2021-07-15 for the id number 114" #unchanged

[1] "The survey does not exist for the day before 2021-06-27 for the id number 115" #unchanged

[1] "The survey does not exist for the day before 2021-07-01 for the id number 115" #unchanged

[1] "The survey does not exist for the day before 2021-07-04 for the id number 115" #unchanged

[1] "The survey does not exist for the day before 2021-06-24 for the id number 112" #changed

[1] "The survey does not exist for the day before 2021-06-28 for the id number 112" #changed

[1] "The survey does not exist for the day before 2021-07-04 for the id number 112" #changed

[1] "The survey does not exist for the day before 2021-07-09 for the id number 117" #changed

[1] "The survey does not exist for the day before 2021-07-16 for the id number 117" #changed

[1] "The survey does not exist for the day before 2021-07-24 for the id number 117" #changed

[1] "The survey does not exist for the day before 2021-07-26 for the id number 117" #changed

[1] "The survey does not exist for the day before 2021-08-20 for the id number 119"
[1] "The survey does not exist for the day before 2021-08-20 for the id number 119"
[1] "The survey does not exist for the day before 2021-08-08 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-08 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-13 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-13 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-15 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-15 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-21 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-21 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-25 for the id number 118"
[1] "The survey does not exist for the day before 2021-08-25 for the id number 118"
[1] "The survey does not exist for the day before 2021-09-01 for the id number 118"
[1] "The survey does not exist for the day before 2021-09-01 for the id number 118"
[1] "The survey does not exist for the day before 2021-09-05 for the id number 118"
[1] "The survey does not exist for the day before 2021-09-05 for the id number 118"
[1] "The survey does not exist for the day before 2021-09-02 for the id number 124"
[1] "The survey does not exist for the day before 2021-09-02 for the id number 124"
[1] "The survey does not exist for the day before 2021-09-05 for the id number 124"
[1] "The survey does not exist for the day before 2021-09-05 for the id number 124"
[1] "The survey does not exist for the day before 2021-08-26 for the id number 125"
[1] "The survey does not exist for the day before 2021-08-26 for the id number 125"
[1] "The survey does not exist for the day before 2021-08-28 for the id number 125"
[1] "The survey does not exist for the day before 2021-08-28 for the id number 125"
[1] "The survey does not exist for the day before 2022-01-20 for the id number 125"
[1] "The survey does not exist for the day before 2022-01-20 for the id number 125"
[1] "The survey does not exist for the day before 2021-08-27 for the id number 128"
[1] "The survey does not exist for the day before 2021-08-27 for the id number 128"
[1] "The survey does not exist for the day before 2021-09-04 for the id number 128"
[1] "The survey does not exist for the day before 2021-09-04 for the id number 128"
[1] "The survey does not exist for the day before 2021-09-11 for the id number 128"
[1] "The survey does not exist for the day before 2021-09-11 for the id number 128"
[1] "The survey does not exist for the day before 2021-09-03 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-03 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-11 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-11 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-13 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-13 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-25 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-25 for the id number 130"
[1] "The survey does not exist for the day before 2021-09-19 for the id number 129"
[1] "The survey does not exist for the day before 2021-09-19 for the id number 129"
[1] "The survey does not exist for the day before 2021-09-21 for the id number 129"
[1] "The survey does not exist for the day before 2021-09-21 for the id number 129"
[1] "The survey does not exist for the day before 2021-09-27 for the id number 129"
[1] "The survey does not exist for the day before 2021-09-27 for the id number 129"
[1] "The survey does not exist for the day before 2021-09-12 for the id number 127"
[1] "The survey does not exist for the day before 2021-09-12 for the id number 127"
[1] "The survey does not exist for the day before 2021-10-21 for the id number 132"
[1] "The survey does not exist for the day before 2021-10-21 for the id number 132"
[1] "The survey does not exist for the day before 2021-10-23 for the id number 132"
[1] "The survey does not exist for the day before 2021-10-23 for the id number 132"
[1] "The survey does not exist for the day before 2021-11-04 for the id number 132"
[1] "The survey does not exist for the day before 2021-11-04 for the id number 132"
[1] "The survey does not exist for the day before 2021-11-06 for the id number 132"
[1] "The survey does not exist for the day before 2021-11-06 for the id number 132"
[1] "The survey does not exist for the day before 2021-11-06 for the id number 133"
[1] "The survey does not exist for the day before 2021-11-06 for the id number 133"
[1] "The survey does not exist for the day before 2021-11-18 for the id number 133"
[1] "The survey does not exist for the day before 2021-11-18 for the id number 133"
[1] "The survey does not exist for the day before 2021-12-09 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-09 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-16 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-16 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-20 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-20 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-22 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-22 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-25 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-25 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-30 for the id number 136"
[1] "The survey does not exist for the day before 2021-12-30 for the id number 136"
[1] "The survey does not exist for the day before 2022-02-06 for the id number 138"
[1] "The survey does not exist for the day before 2022-02-06 for the id number 138"
[1] "The survey does not exist for the day before 2022-02-11 for the id number 138"
[1] "The survey does not exist for the day before 2022-02-11 for the id number 138"
[1] "The survey does not exist for the day before 2022-02-10 for the id number 140"
[1] "The survey does not exist for the day before 2022-02-10 for the id number 140"
[1] "The survey does not exist for the day before 2022-02-06 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-06 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-14 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-14 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-21 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-21 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-24 for the id number 139"
[1] "The survey does not exist for the day before 2022-02-24 for the id number 139"
[1] "The survey does not exist for the day before 2022-01-31 for the id number 143"
[1] "The survey does not exist for the day before 2022-01-31 for the id number 143"
[1] "The survey does not exist for the day before 2022-02-12 for the id number 143"
[1] "The survey does not exist for the day before 2022-02-12 for the id number 143"
[1] "The survey does not exist for the day before 2022-02-02 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-02 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-04 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-04 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-06 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-06 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-09 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-09 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-21 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-21 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-25 for the id number 141"
[1] "The survey does not exist for the day before 2022-02-25 for the id number 141"
[1] "The survey does not exist for the day before 2022-03-07 for the id number 146"
[1] "The survey does not exist for the day before 2022-03-07 for the id number 146"
[1] "The survey does not exist for the day before 2022-03-27 for the id number 146"
[1] "The survey does not exist for the day before 2022-03-27 for the id number 146"
[1] "The survey does not exist for the day before 2022-03-14 for the id number 145"
[1] "The survey does not exist for the day before 2022-03-14 for the id number 145"
[1] "The survey does not exist for the day before 2022-04-24 for the id number 147"
[1] "The survey does not exist for the day before 2022-04-24 for the id number 147"
[1] "The survey does not exist for the day before 2022-05-21 for the id number 148"
[1] "The survey does not exist for the day before 2022-05-21 for the id number 148"
[1] "The survey does not exist for the day before 2022-05-29 for the id number 148"
[1] "The survey does not exist for the day before 2022-05-29 for the id number 148"
[1] "The survey does not exist for the day before 2022-06-20 for the id number 148"
[1] "The survey does not exist for the day before 2022-06-20 for the id number 148"
[1] "The survey does not exist for the day before 2022-05-31 for the id number 149"
[1] "The survey does not exist for the day before 2022-05-31 for the id number 149"
[1] "The survey does not exist for the day before 2022-05-31 for the id number 150"
[1] "The survey does not exist for the day before 2022-05-31 for the id number 150"
[1] "The survey does not exist for the day before 2022-06-07 for the id number 150"
[1] "The survey does not exist for the day before 2022-06-07 for the id number 150"
[1] "The survey does not exist for the day before 2022-06-17 for the id number 150"
[1] "The survey does not exist for the day before 2022-06-17 for the id number 150"
[1] "The survey does not exist for the day before 2022-07-11 for the id number 152"
[1] "The survey does not exist for the day before 2022-07-11 for the id number 152"
[1] "The survey does not exist for the day before 2022-07-14 for the id number 152"
[1] "The survey does not exist for the day before 2022-07-14 for the id number 152"
[1] "The survey does not exist for the day before 2022-06-26 for the id number 154"
[1] "The survey does not exist for the day before 2022-06-26 for the id number 154"
[1] "The survey does not exist for the day before 2022-06-30 for the id number 154"
[1] "The survey does not exist for the day before 2022-06-30 for the id number 154"
[1] "The survey does not exist for the day before 2022-07-06 for the id number 154"
[1] "The survey does not exist for the day before 2022-07-06 for the id number 154"
[1] "The survey does not exist for the day before 2022-07-09 for the id number 154"
[1] "The survey does not exist for the day before 2022-07-09 for the id number 154"
[1] "The survey does not exist for the day before 2022-07-13 for the id number 154"
[1] "The survey does not exist for the day before 2022-07-13 for the id number 154"
[1] "The survey does not exist for the day before 2022-06-28 for the id number 153"
[1] "The survey does not exist for the day before 2022-06-28 for the id number 153"
[1] "The survey does not exist for the day before 2022-07-17 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-17 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-22 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-22 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-24 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-24 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-26 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-26 for the id number 155"
[1] "The survey does not exist for the day before 2022-07-15 for the id number 156"
[1] "The survey does not exist for the day before 2022-07-15 for the id number 156"
[1] "The survey does not exist for the day before 2022-07-21 for the id number 157"
[1] "The survey does not exist for the day before 2022-07-21 for the id number 157"
[1] "The survey does not exist for the day before 2022-07-28 for the id number 160"
[1] "The survey does not exist for the day before 2022-07-28 for the id number 160"
[1] "The survey does not exist for the day before 2022-07-31 for the id number 161"
[1] "The survey does not exist for the day before 2022-07-31 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-10 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-10 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-12 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-12 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-14 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-14 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-24 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-24 for the id number 161"
[1] "The survey does not exist for the day before 2022-08-10 for the id number 162"
[1] "The survey does not exist for the day before 2022-08-10 for the id number 162"
[1] "The survey does not exist for the day before 2022-08-22 for the id number 162"
[1] "The survey does not exist for the day before 2022-08-22 for the id number 162"
[1] "The survey does not exist for the day before 2022-08-21 for the id number 163"
[1] "The survey does not exist for the day before 2022-08-21 for the id number 163"
[1] "The survey does not exist for the day before 2022-08-29 for the id number 158"
[1] "The survey does not exist for the day before 2022-08-29 for the id number 158"
[1] "The survey does not exist for the day before 2022-09-04 for the id number 158"
[1] "The survey does not exist for the day before 2022-09-04 for the id number 158"
[1] "The survey does not exist for the day before 2022-09-04 for the id number 165"
[1] "The survey does not exist for the day before 2022-09-04 for the id number 165"
[1] "The survey does not exist for the day before 2022-09-13 for the id number 165"
[1] "The survey does not exist for the day before 2022-09-13 for the id number 165"
[1] "The survey does not exist for the day before 2022-09-07 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-07 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-12 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-12 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-15 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-15 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-18 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-18 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-30 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-30 for the id number 164"
[1] "The survey does not exist for the day before 2022-09-25 for the id number 166"
[1] "The survey does not exist for the day before 2022-09-25 for the id number 166"
[1] "The survey does not exist for the day before 2022-10-19 for the id number 167"
[1] "The survey does not exist for the day before 2022-10-19 for the id number 167"
[1] "The survey does not exist for the day before 2022-09-25 for the id number 168"
[1] "The survey does not exist for the day before 2022-09-25 for the id number 168"
[1] "The survey does not exist for the day before 2022-09-28 for the id number 168"
[1] "The survey does not exist for the day before 2022-09-28 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-09 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-09 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-19 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-19 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-26 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-26 for the id number 168"
[1] "The survey does not exist for the day before 2022-10-02 for the id number 169"
[1] "The survey does not exist for the day before 2022-10-02 for the id number 169"
[1] "The survey does not exist for the day before 2022-10-14 for the id number 169"
[1] "The survey does not exist for the day before 2022-10-14 for the id number 169"
[1] "The survey does not exist for the day before 2022-10-16 for the id number 169"
[1] "The survey does not exist for the day before 2022-10-16 for the id number 169"
[1] "The survey does not exist for the day before 2022-10-19 for the id number 170"
[1] "The survey does not exist for the day before 2022-10-19 for the id number 170"
[1] "The survey does not exist for the day before 2022-10-17 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-17 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-21 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-21 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-26 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-26 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-28 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-28 for the id number 171"
[1] "The survey does not exist for the day before 2022-11-04 for the id number 171"
[1] "The survey does not exist for the day before 2022-11-04 for the id number 171"
[1] "The survey does not exist for the day before 2022-11-06 for the id number 171"
[1] "The survey does not exist for the day before 2022-11-06 for the id number 171"
[1] "The survey does not exist for the day before 2022-10-29 for the id number 172"
[1] "The survey does not exist for the day before 2022-10-29 for the id number 172"
[1] "The survey does not exist for the day before 2022-11-04 for the id number 172"
[1] "The survey does not exist for the day before 2022-11-04 for the id number 172"
[1] "The survey does not exist for the day before 2022-11-06 for the id number 172"
[1] "The survey does not exist for the day before 2022-11-06 for the id number 172"
[1] "The survey does not exist for the day before 2022-10-27 for the id number 173"
[1] "The survey does not exist for the day before 2022-10-27 for the id number 173"
[1] "The survey does not exist for the day before 2022-11-09 for the id number 173"
[1] "The survey does not exist for the day before 2022-11-09 for the id number 173"
[1] "The survey does not exist for the day before 2022-11-16 for the id number 173"
[1] "The survey does not exist for the day before 2022-11-16 for the id number 173"
[1] "The survey does not exist for the day before 2023-02-04 for the id number 176"
[1] "The survey does not exist for the day before 2023-02-04 for the id number 176"
[1] "The survey does not exist for the day before 2023-02-17 for the id number 175"
[1] "The survey does not exist for the day before 2023-02-17 for the id number 175"
[1] "The survey does not exist for the day before 2023-02-27 for the id number 175"
[1] "The survey does not exist for the day before 2023-02-27 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-03 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-03 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-11 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-11 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-13 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-13 for the id number 175"
[1] "The survey does not exist for the day before 2023-03-23 for the id number 179"
[1] "The survey does not exist for the day before 2023-03-23 for the id number 179"
[1] "The survey does not exist for the day before 2023-04-08 for the id number 179"
[1] "The survey does not exist for the day before 2023-04-08 for the id number 179"
[1] "The survey does not exist for the day before 2023-04-10 for the id number 179"
[1] "The survey does not exist for the day before 2023-04-10 for the id number 179"
[1] "The survey does not exist for the day before 2023-04-19 for the id number 179"
[1] "The survey does not exist for the day before 2023-04-19 for the id number 179"
[1] "The survey does not exist for the day before 2023-03-23 for the id number 180"
[1] "The survey does not exist for the day before 2023-03-23 for the id number 180"
[1] "The survey does not exist for the day before 2023-03-29 for the id number 180"
[1] "The survey does not exist for the day before 2023-03-29 for the id number 180"
[1] "The survey does not exist for the day before 2023-03-31 for the id number 180"
[1] "The survey does not exist for the day before 2023-03-31 for the id number 180"
[1] "The survey does not exist for the day before 2023-04-15 for the id number 180"
[1] "The survey does not exist for the day before 2023-04-15 for the id number 180"
[1] "The survey does not exist for the day before 2023-03-22 for the id number 181"
[1] "The survey does not exist for the day before 2023-03-22 for the id number 181"
[1] "The survey does not exist for the day before 2023-04-02 for the id number 181"
[1] "The survey does not exist for the day before 2023-04-02 for the id number 181"
[1] "The survey does not exist for the day before 2023-04-15 for the id number 181"
[1] "The survey does not exist for the day before 2023-04-15 for the id number 181"
[1] "The survey does not exist for the day before 2023-04-12 for the id number 182"
[1] "The survey does not exist for the day before 2023-04-12 for the id number 182"
[1] "The survey does not exist for the day before 2023-04-16 for the id number 182"
[1] "The survey does not exist for the day before 2023-04-16 for the id number 182"
[1] "The survey does not exist for the day before 2023-05-13 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-13 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-16 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-16 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-23 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-23 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-26 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-26 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-29 for the id number 184"
[1] "The survey does not exist for the day before 2023-05-29 for the id number 184"
[1] "There are 530 surveys where the same daterated is recorded, by participant"




#Remove PM Duplicates
```{r}
#PM Duplicates 
#ID 103 
pm_data %>%
  filter(ID == 103 & daterated == ymd("2021-04-20"))

pm_data <- pm_data[!(pm_data$ID == 103 & pm_data$daterated == "2021-04-20" & pm_data$time_pm == ""), ] 

pm_data %>%
  filter(ID == 103 & daterated == ymd("2021-04-24"))

pm_data <- pm_data[!(pm_data$ID == 103 & pm_data$daterated == "2021-04-24" & pm_data$time_pm == ""), ] 

pm_data %>%
  filter(ID == 103 & daterated == ymd("2021-04-26"))

pm_data <- pm_data[!(pm_data$ID == 103 & pm_data$daterated == "2021-04-26" & pm_data$time_pm == "0:12"), ] 
```

#remove IDs = NA 
```{r}
#note that these four didn't seem to work 
#am_data <- am_data[!(is.na(am_data$ID)), ] 
#am_data <- am_data[!(am_data$ID == NA), ] 
#subset(am_data, !is.na(ID))
#am_data[!is.na(am_data$ID),]
#am_data %>% drop_na(ID)
#am_data %>% drop_na(daterated)
```


#Anisha's way to investigate IDs in result_am and result_pm in which obs >1 
#Note that she wrote this with the old column names - will adjust based on final column naming scheme 
pm_data %>%  
  filter(id==[INSERT ID] & daterated==mdy("[INSERT DATE]"))

am_data %>%
  filter(id==[INSERT ID] & daterated==mdy("[INSERT DATE]"))
  
Remove by time using subset. If they are exactly the same, keep the earliest one. If not, keep the most complete one. 


#Drop Time Variable 
```{r}
am_data = subset(am_data, select=-c(time_am))

pm_data = subset(pm_data, select=-c(time_pm))
```

#drop ID 127 per Annie Griffith's recommendation (not much data for this ID)
```{r}

am_data <- subset(am_data, ID != 127)

pm_data <- subset(pm_data, ID != 127)

```



#IDs in both am and pm datasets: 
[1] "101"       "102"       "103"       "104"       "105"       "106"       "107"       "108"       "109"      
[10] "111"       "112"       "113"       "114"       "115"       "116"       "117"       "118"       "119"      
[19] "120"       "121"       "122"       "123"       "124"       "125"       "125b"      "125c"      "125d"     
[28] "126"       "127"       "127 (new)" "128"       "129"       "130"       "131"       "132"       "133"      
[37] "134"       "134b"      "135"       "136"       "138"       "139"       "139b"      "140"       "141"      
[46] "142"       "142b"      "143"       "144"       "145"       "146"       "147"       "148"       "149"      
[55] "150"       "152"       "153"       "154"       "155"       "156"       "157"       "158"       "159"      
[64] "160"       "161"       "162"       "163"       "164"       "165"       "166"       "166a"      "166b"     
[73] "167"       "168"       "169"       "170"       "171"       "172"       "173"       "174"       "175"      
[82] "176"       "177"       "178"       "179"       "180"       "181"       "182"       "183"       "184"      
[91] "185"  



