---
title: "UKAlc_Daily_Lab_Cycle_Merge"
author: "Anna Patterson"
date: "2024-01-16"
output: html_document
---

# Load Libraries 
```{r}
library(tidyverse)
library(dplyr)
library(tidyr)
library(stringr)
library(janitor)
library(lubridate) 
library(ggplot2)
```

# Add in study day variable 
```{r}
am_data_clean <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/03_cleaned_data/am_data_cleaned_AP.csv")

pm_data_clean <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/03_cleaned_data/pm_data_cleaned_AP.csv")

am_data_clean <- am_data_clean %>% group_by(ID) %>%
  mutate(day_in_study = seq(length = n())) 

pm_data_clean <- pm_data_clean %>% group_by(ID) %>%
  mutate(day_in_study = seq(length = n())) 
```

#### Merge in lab visit data 

```{r}
#Lab Visit Data 
labvisit <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_LABVISITS/01_raw_data/Mini Dataset 1.8.24.csv") 
```

## rename vars to match am_data and pm_data and delete irrelevant columns 
```{r}
names(labvisit)[names(labvisit) == "Subject"] <- "ID"
labvisit <- subset(labvisit, select = -Weight)
```

## save cleaned file as csv 
```{r}
write.csv(labvisit, "~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_LABVISITS/03_cleaned_data/labvisit_cleaned_AP.csv", row.names=TRUE)

 labvisit <- read_csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_LABVISITS/03_cleaned_data/labvisit_cleaned_AP.csv")
```

## merge in lab visit dates 
```{r} 
#read csv for alcohol session dates as ordered by PHASE not sequential order 
alc.visit.dates <- read_xlsx("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_LABVISITS/01_raw_data/Alc_Visits_By_Follicular_Phase.xlsx")

#new column for presence of lab visit 
alc.visit.dates$labvisit <- 1 

labvisit <- merge(alc.visit.dates, labvisit, by = c("ID"), all = T) 
#question - below isn't working 
labvisit$Early Follicular Visit <- ymd(labvisit$Early Follicular Visit, na.rm = TRUE)
labvisit$Late Follicular Visit <- ymd(labvisit$Late Follicular Visit, na.rm = TRUE)
```

## re-format 
```{r}

#make new df with early foll and late foll lab visit days 
labvisit_EF <- labvisit %>% select(ID, starts_with("E1"))
labvisit_LF <- labvisit %>% select(ID, starts_with("E2"))

labvisit_EF <- labvisit_EF %>% rename_all(~ gsub("^E1", "", .))
labvisit_LF <- labvisit_LF %>% rename_all(~ gsub("^E2", "", .))

names(labvisit_EF)[names(labvisit_EF) == "S1"] <- "daterated"
names(labvisit_LF)[names(labvisit_LF) == "S2"] <- "daterated"

labvisit_EF$follphase <- 1 
labvisit_LF$follphase <- 2

labvisit_clean <- rbind(labvisit_EF, labvisit_LF) 

labvisit_clean <- labvisit_clean %>% arrange(ID)
```

## merge file with daily data 
```{r}
labvisit.am.data.merge <- merge(labvisit_clean, am_data_clean, by = c("ID", "daterated"), all = T) #question - add daterated now 
labvisit.pm.data.merge <- merge(labvisit_clean, pm_data_clean, by =c("ID", "daterated"), all = T)
```

## merge in salivary hormone data 
```{r}
hormones <- read_xlsx("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_HORM/02_data_prep_workspace/Salivary_Results_For_Import.xlsx")
```

#add "day in study column" for hormone data and save new csv 
```{r}
hormones <- separate(hormones, col = Sample, into = c("ID", "day_in_study"), sep = "-")

write.csv(hormones, "~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_HORM/02_data_prep_workspace/Salivary_Hormones_StudyDays.csv", row.names=TRUE)
```

# merge hormone data w am, pm, and lab visit data 
```{r}
am_data_clean_horm <- merge(labvisit.am.data.merge, hormones, by = c("ID", "day_in_study"), all = T)
pm_data_clean_horm <- merge(labvisit.pm.data.merge, hormones, by = c("ID", "day_in_study"), all = T)
```


#Add in cycle day 
```{r}

cycle.day <- read.csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/UKAlc.Cycle.Day.csv")

```

#Merge in cycle day data 
```{r}
#use janitor package to make sure the 2 datasets can be merged
#return=mismatch will return only columns that cannot merge

cycle.day$daterated <- mdy(cycle.day$daterated)

cycleday.am.merge <- merge(cycle.day, labvisit.am.data.merge, by = c("ID", "daterated"), all = T)
cycleday.pm.merge <- merge(cycle.day, labvisit.pm.data.merge, by = c("ID", "daterated"), all = T)
```
#Add in LH Data
```{r}
LH.Count <- read.csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_DAILY/02_data_prep_workspace/UKAlc.LH.Data.csv")

LH.Count$daterated <- mdy(LH.Count$daterated)

cycleday.am.merge <- merge(LH.Count, cycleday.am.merge, by = c("ID", "daterated"), all = T)
cycleday.pm.merge <- merge(LH.Count, cycleday.pm.merge, by = c("ID", "daterated"), all = T)

write_csv(cycleday.am.merge, "Cycle_Day_LH_menses_am_labvisit.csv")
write_csv(cycleday.pm.merge, "Cycle_Day_LH_menses_pm_labvisit.csv")
```


```{r cyclephase_count}

cycleday.am.merge <- cycleday.am.merge %>% 
  mutate(midluteal_count = ifelse(cycleday >= -9 & cycleday <= -5, 1, 0),
         perimenstrual_count = ifelse(cycleday >=-3 & cycleday <=2, 1, 0),
         midfol_count = ifelse(cycleday >=4 & cycleday <=7, 1, 0),
         periov_count = ifelse(cycleday >= -15 & cycleday <= -12, 1, 0))

#add a non-dummy coded variable with all of cycle phase info above, which will be useful for future visualizations and summaries
cycleday.am.merge <- cycleday.am.merge %>% mutate(cyclephase_count = case_when(periov_count==1 ~ 1,
                                                     midluteal_count==1 ~ 2,
                                                     perimenstrual_count==1 ~ 3,
                                                     midfol_count==1 ~ 4,
                                                     TRUE ~ as.numeric(NA)))

cycleday.pm.merge <- cycleday.pm.merge %>% 
  mutate(midluteal_count = ifelse(cycleday >= -9 & cycleday <= -5, 1, 0),
         perimenstrual_count = ifelse(cycleday >=-3 & cycleday <=2, 1, 0),
         midfol_count = ifelse(cycleday >=4 & cycleday <=7, 1, 0),
         periov_count = ifelse(cycleday >= -15 & cycleday <= -12, 1, 0))

#add a non-dummy coded variable with all of cycle phase info above, which will be useful for future visualizations and summaries
cycleday.pm.merge <- cycleday.pm.merge %>% mutate(cyclephase_count = case_when(periov_count==1 ~ 1,
                                                     midluteal_count==1 ~ 2,
                                                     perimenstrual_count==1 ~ 3,
                                                     midfol_count==1 ~ 4,
                                                     TRUE ~ as.numeric(NA)))



```
#This LH cyclephase code is adapted from github repository: code_templates/prep_Cycle Phase Coding 5 phase - ADHD-KY.Rmd starting at step 5a 
```{r cyclephase_LH}

cycleday.am.merge <- cycleday.am.merge %>% 
  mutate(midluteal_LH = ifelse(daycountLH >= 6 & daycountLH <= 10, 1, 0),
         perimenstrual_LH = ifelse(cycleday >=-3 & cycleday <=2, 1, 0), #note perimenstrual is based on cycleday
         midfol_LH = ifelse(daycountLH >=-7 & daycountLH <=-3, 1, 0),
         periov_LH = ifelse(daycountLH >= -2 & daycountLH <= 1, 1, 0),
         earlylut_LH = ifelse(daycountLH >= 2 & daycountLH <= 5, 1, 0))

#fill out the dummy code, so that if any phase is 1, all others should be 0 (not NA)
cycleday.am.merge <- cycleday.am.merge %>%
  rowwise() %>%
  mutate(sumdummy = sum(midfol_LH,
                        periov_LH,
                        earlylut_LH,
                        perimenstrual_LH,
                        midluteal_LH, na.rm = T)) %>% 
  #if all phases=0, make the midluteal_LH variable NA instead of 0,
  #if perimenstrual by menses count = 1, change midluteal_LH to 0 instead of NA to fill out structural set,
  #otherwise, keep as is
  mutate(midluteal_LH = case_when(sumdummy==0 ~ as.numeric(NA),
                                  sumdummy==1 & perimenstrual_LH==1 ~ 0,
                                  TRUE ~ midluteal_LH), 
         #same for midfol
         midfol_LH = case_when(sumdummy==0 ~ as.numeric(NA),
                               sumdummy==1 & perimenstrual_LH==1 ~ 0,
                               TRUE ~ midfol_LH), 
          #same for periov
         periov_LH = case_when(sumdummy==0 ~ as.numeric(NA),
                               sumdummy==1 & perimenstrual_LH==1 ~ 0,
                               TRUE ~ periov_LH),
         earlylut_LH = case_when(sumdummy==0 ~ as.numeric(NA),
                                  sumdummy==1 & perimenstrual_LH==1 ~ 0,
                                  TRUE ~ earlylut_LH), 
         #if any other phase is 1, fill out perimenstrual to be 0
         perimenstrual_LH = case_when(sumdummy==0 ~ as.numeric(NA), 
                                        sumdummy==1 & midfol_LH==1 ~ 0,
                                        sumdummy==1 & periov_LH==1 ~ 0,
                                      sumdummy==1 & earlylut_LH==1 ~ 0,
                                        sumdummy==1 & midluteal_LH==1 ~ 0,
                                        TRUE ~ perimenstrual_LH))

#add a non-dummy coded variable with all of cycle phase info above, which will be useful for future visualizations and summaries
cycleday.am.merge <- cycleday.am.merge %>% mutate(cyclephase_LH = case_when(periov_LH==1 ~ 1,
                                                                        earlylut_LH==1 ~ 2,
                                                     midluteal_LH==1 ~ 3,
                                                     perimenstrual_LH==1 ~ 4,
                                                     midfol_LH==1 ~ 5,
                                                     TRUE ~ as.numeric(NA)))

#add names for easier visualization
cycleday.am.merge <- cycleday.am.merge %>% mutate(cyclephase_LHnames = factor(cyclephase_LH, 
                                                                              levels = c(1,2,3,4,5),
                                                                              labels = c("periov",
                                                                                         "earlylut",
                                                                                         "midlut",
                                                                                         "perimens",
                                                                                         "midfol")))

```

```{r}

#check overlaps: goal is to only have 6 possible group combinations here (1 row per dummy coded phase, then a row where ALL are NA)
cycleday.am.merge %>%
  group_by(periov_LH, earlylut_LH, midluteal_LH, perimenstrual_LH, midfol_LH) %>%
  summarize(n=n())
#make note of errors


#example code to review midfol_LH and perimenstrual_LH overlaps, if they exist
cycleday.am.merge %>%
  filter(midfol_LH==1) %>%
  filter(perimenstrual_LH==1) %>%
  select(id, daterated, posLHtoday, daycountLH,
         menstrualbleeding,
         firstdayofperiod, cycleday,
         midfol_LH, periov_LH, earlylut_LH,
         midluteal_LH, perimenstrual_LH) %>%
  View()



```                                             

#edit days that got double-counted
```{r}

cycleday.am.merge  <- cycleday.am.merge  %>%
  #if perimenstrual by firstdayofperiod and midfol by pre-LH count are both 1, perimen wins, make midfol=0
  mutate(midfol_LH = case_when(perimenstrual_LH==1 ~ 0,
                                        TRUE ~ midfol_LH)) 

#review midlut and perimens overlaps - can override midluteal with perimens IF luteal phase is short but still seems normal (such as 9-10 days)
## make notes of any SUPER short luteal phases (like 4-5 days) that you might want to flag for anovulation
cycleday.am.merge %>% filter(midluteal_LH==1 & perimenstrual_LH==1) %>% 
  select(ID, daterated, daycountLH, cycleday, midluteal_LH, perimenstrual_LH)

#code for if you are ready to override midluteals with perimens
cycleday.am.merge  <- cycleday.am.merge  %>%
  #if perimenstrual by firstdayofperiod and midlut by count after LH test are both 1, perimen wins, make midlut=0
  mutate(midluteal_LH = case_when(perimenstrual_LH==1 ~ 0,
                                        TRUE ~ midluteal_LH)) 

## ANY OTHER COMBOS need hand review!!

#good practice to review again and ensure that dummy code is fixed
cycleday.am.merge %>%
  group_by(periov_LH, earlylut_LH, midluteal_LH, perimenstrual_LH, midfol_LH) %>%
  summarize(n=n())

```

```{r}

cycleday.pm.merge  <- cycleday.pm.merge  %>%
  #if perimenstrual by firstdayofperiod and midfol by pre-LH count are both 1, perimen wins, make midfol=0
  mutate(midfol_LH = case_when(perimenstrual_LH==1 ~ 0,
                                        TRUE ~ midfol_LH)) 

#review midlut and perimens overlaps - can override midluteal with perimens IF luteal phase is short but still seems normal (such as 9-10 days)
## make notes of any SUPER short luteal phases (like 4-5 days) that you might want to flag for anovulation
cycleday.pm.merge %>% filter(midluteal_LH==1 & perimenstrual_LH==1) %>% 
  select(ID, daterated, daycountLH, cycleday, midluteal_LH, perimenstrual_LH)

#code for if you are ready to override midluteals with perimens
cycleday.pm.merge  <- cycleday.pm.merge  %>%
  #if perimenstrual by firstdayofperiod and midlut by count after LH test are both 1, perimen wins, make midlut=0
  mutate(midluteal_LH = case_when(perimenstrual_LH==1 ~ 0,
                                        TRUE ~ midluteal_LH)) 

## ANY OTHER COMBOS need hand review!!

#good practice to review again and ensure that dummy code is fixed
cycleday.pm.merge %>%
  group_by(periov_LH, earlylut_LH, midluteal_LH, perimenstrual_LH, midfol_LH) %>%
  summarize(n=n())

```     

## save new cycle day am and pm files 
```{r}
cycleday.am.merge %>% write.csv("~/Library/CloudStorage/Box-Box/00 - CLEAR Lab (Locked Folders)/02 - Data Management, Analysis, and Papers/Studies_Projects/UKALC/02_datasets/UKALC_HORM/02_data_prep_workspace/Cycleday.am.LH.menses.data.csv")
```


#as factor for each variable, then rename levels as factors - update data dictionary so you know max/min when factoring. Then do as numeric. It may automatically do numeric but double-check. 
#Calculate luteal phase by subtracting the period start date column by posov_pred column but group by person first! 

